---
title: "Temporal Pollinator Exclusion Experiment"
---

```{r include=FALSE}
library(dplyr)
library(readr)
library(readxl)
library(emmeans)
library(nlme)
```

# Load Data: Floral Traits and Plant Reproductive Success

## Veberöd 2022

```{r}
data_phenotypes_veberod_2022 <- read_rds(paste0(here::here("Data/RDS_Objects/Data_Phenotypes_Veberod_2022.rds")))
```

```{r}
data_phenotypes_veberod_2022 <- data_phenotypes_veberod_2022 %>% 
  filter(Block != "NA")
```

# Compare Floral Traits and Plant Reproductive Success Across Experimental Treatments

```{r}
data_veberod_2022_compare_treatments_floral_traits <- list()

for (response_vars in c("Stem_Height", "Stickidium", "Corolla_Diameter", "Tube_Width", "Tube_Length", "NSD", "Total_Flowers")) {

  anova_model <- lme(fixed = as.formula(paste0(response_vars, " ~ Treatment")),
                     random = ~ 1 | Plant_ID,
                     na.action = na.omit,
                     data = data_phenotypes_veberod_2022)
  
  anova_result <- anova(anova_model)
  
  anova_post_hoc <- pairs(emmeans(anova_model, ~ Treatment), adjust = "bonferroni")
  
  data_veberod_2022_compare_treatments_floral_traits[[response_vars]] <- list(anova_result, anova_post_hoc)
}
```

```{r}
data_veberod_2022_compare_treatments_plant_reproduction <- list()

for (response_vars in c("Total_Fruits", "Mean_Seeds_Weight", "Fruit_Yield_Total_Fruits")) {

  anova_model <- lme(fixed = as.formula(paste0(response_vars, " ~ Treatment")),
                     random = ~ 1 | Plant_ID,
                     na.action = na.omit,
                     data = data_phenotypes_veberod_2022)
  
  anova_result <- anova(anova_model)
  
  anova_post_hoc <- pairs(emmeans(anova_model, ~ Treatment), adjust = "bonferroni")
  
  data_veberod_2022_compare_treatments_plant_reproduction[[response_vars]] <- list(anova_result, anova_post_hoc)
}
```

# Compare Phenotypic Selection on Floral Traits Across Experimental Treatments

```{r}
data_phenotypes_veberod_2022 <- read_rds(paste0(here::here("Data/RDS_Objects/Data_Phenotypes_Veberod_2022.rds")))
```

## No Exclusion of Pollinators (NO) vs. Complete Exclusion of Pollinators (CE)

```{r}
data_veberod_2022_open_closed_ancova <- nlme::lme(Relative_Fruit_Yield_Total_Fruits ~
                                                           Stem_Height_Mean_Centred +
                                                           Corolla_Diameter_Mean_Centred +
                                                           Tube_Width_Mean_Centred +
                                                           Tube_Length_Mean_Centred +
                                                           NSD_Mean_Centred +
                                                           Stickidium_Mean_Centred +
                                                           Total_Flowers_Mean_Centred +
                                                           Treatment +
                                                           Stem_Height_Mean_Centred:Treatment +
                                                           Corolla_Diameter_Mean_Centred:Treatment +
                                                           Tube_Width_Mean_Centred:Treatment +
                                                           Tube_Length_Mean_Centred:Treatment +
                                                           NSD_Mean_Centred:Treatment +
                                                           Stickidium_Mean_Centred:Treatment +
                                                           Total_Flowers_Mean_Centred:Treatment,
                                                         random = ~ 1 | Plant_ID,
                                                         na.action = na.omit,
                                                         data = data_phenotypes_veberod_2022 %>% 
                                                           filter(Treatment %in% c("Open_Control", "Always_Caged")))
```

```{r}
data_veberod_2022_open_closed <- nlme::lme(Relative_Fruit_Yield_Total_Fruits ~
                                                           Stem_Height_Mean_Centred +
                                                           Corolla_Diameter_Mean_Centred +
                                                           Tube_Width_Mean_Centred +
                                                           Tube_Length_Mean_Centred +
                                                           NSD_Mean_Centred +
                                                           Stickidium_Mean_Centred +
                                                           Total_Flowers_Mean_Centred,
                                                         random = ~ 1 | Plant_ID,
                                                         na.action = na.omit,
                                                         data = data_phenotypes_veberod_2022 %>% 
                                                           filter(Treatment %in% c("Open_Control", "Always_Caged")))
```

```{r warning=FALSE}
test_variation_open_closed <- compare_performance(data_veberod_2022_open_closed_ancova, data_veberod_2022_open_closed)
```

## Exclusion of Diurnal Pollinators (DE) vs. Exclusion of Nocturnal Pollinators (NE)

```{r}
data_veberod_2022_day_night_ancova <- nlme::lme(Relative_Fruit_Yield_Total_Fruits ~
                                                           Stem_Height_Mean_Centred +
                                                           Corolla_Diameter_Mean_Centred +
                                                           Tube_Width_Mean_Centred +
                                                           Tube_Length_Mean_Centred +
                                                           NSD_Mean_Centred +
                                                           Stickidium_Mean_Centred +
                                                           Total_Flowers_Mean_Centred +
                                                           Treatment +
                                                           Stem_Height_Mean_Centred:Treatment +
                                                           Corolla_Diameter_Mean_Centred:Treatment +
                                                           Tube_Width_Mean_Centred:Treatment +
                                                           Tube_Length_Mean_Centred:Treatment +
                                                           NSD_Mean_Centred:Treatment +
                                                           Stickidium_Mean_Centred:Treatment +
                                                           Total_Flowers_Mean_Centred:Treatment,
                                                         random = ~ 1 | Plant_ID,
                                                         na.action = na.omit,
                                                         data = data_phenotypes_veberod_2022 %>% 
                                                           filter(Treatment %in% c("Day_Caged", "Night_Caged")))
```

```{r}
data_veberod_2022_day_night <- nlme::lme(Relative_Fruit_Yield_Total_Fruits ~
                                                           Stem_Height_Mean_Centred +
                                                           Corolla_Diameter_Mean_Centred +
                                                           Tube_Width_Mean_Centred +
                                                           Tube_Length_Mean_Centred +
                                                           NSD_Mean_Centred +
                                                           Stickidium_Mean_Centred +
                                                           Total_Flowers_Mean_Centred,
                                                         random = ~ 1 | Plant_ID,
                                                         na.action = na.omit,
                                                         data = data_phenotypes_veberod_2022 %>% 
                                                           filter(Treatment %in% c("Day_Caged", "Night_Caged")))
```

```{r warning=FALSE}
test_variation_day_night <- compare_performance(data_veberod_2022_day_night_ancova, data_veberod_2022_day_night)
```

# Load Data: Mean-Standardized Phenotypic Selection Gradients

```{r}
data_selection_gradients_veberod_2022 <- read_rds(paste0(here::here("Data/RDS_Objects/Selection_Gradients_Veberod_2022.rds")))
```

# Mean Value and Error-Corrected Variance of the Mean-Standardized Phenotypic Selection Gradients

## No Exclusion of Pollinators (NO) vs. Complete Exclusion of Pollinators (CE)

```{r warning=FALSE}
data_selection_gradients_veberod_2022_mean_variance_NO_CE <- data_selection_gradients_veberod_2022 %>% 
  group_by(Trait) %>% 
  filter(Treatment %in% c("Open_Control", "Always_Caged")) %>% 
  summarise(Variance_Mean_Selection_Gradient = var(Mean_Selection_Gradient),
            Mean_Mean_SE_Selection_Gradient = mean(Mean_SE_Selection_Gradient^2),
            Difference = Variance_Mean_Selection_Gradient - Mean_Mean_SE_Selection_Gradient,
            Varriance_Corrected_Mean_Selection_Gradient = sqrt(Variance_Mean_Selection_Gradient - Mean_Mean_SE_Selection_Gradient)) %>% 
  mutate_if(is.numeric, round, digits = 4) %>% 
  mutate(Comparison = "NO_CE")
```

## Exclusion of Diurnal Pollinators (DE) vs. Exclusion of Nocturnal Pollinators (NE)

```{r warning=FALSE}
data_selection_gradients_veberod_2022_mean_variance_DE_NE <- data_selection_gradients_veberod_2022 %>% 
  group_by(Trait) %>% 
  filter(Treatment %in% c("Day_Caged", "Night_Caged")) %>% 
  summarise(Variance_Mean_Selection_Gradient = var(Mean_Selection_Gradient),
            Mean_Mean_SE_Selection_Gradient = mean(Mean_SE_Selection_Gradient^2),
            Difference = Variance_Mean_Selection_Gradient - Mean_Mean_SE_Selection_Gradient,
            Varriance_Corrected_Mean_Selection_Gradient = sqrt(Variance_Mean_Selection_Gradient - Mean_Mean_SE_Selection_Gradient)) %>% 
  mutate_if(is.numeric, round, digits = 4) %>% 
  mutate(Comparison = "DE_NE")
```

## Merge Mean Value and Error-Corrected Variance of the Mean-Standardized Phenotypic Selection Gradients

```{r}
data_selection_gradients_mean_variance_experiment <- rbind(data_selection_gradients_veberod_2022_mean_variance_NO_CE,
                                                           data_selection_gradients_veberod_2022_mean_variance_DE_NE)
```

```{r}
saveRDS(data_selection_gradients_mean_variance_experiment, 
        file = paste0(here::here("Data/RDS_Objects/Selection_Gradients_Error_Corrected_Experiment.rds")))
```