---
title: "Figures"
---

```{r include=FALSE}
library(dplyr)
library(ggplot2)
library(ggpp)
library(ggpubr)
library(readr)
library(reshape2)
library(tidyr)
library(stringr)
```

# Load Data: Mean-Standardized Phenotypic Selection Gradients

```{r}
data_selection_gradients_knivsasen_2021 <- read_rds(paste0(here::here("Data/RDS_Objects/Selection_Gradients_Knivsasen_2021.rds")))

data_selection_gradients_knivsasen_2022 <- read_rds(paste0(here::here("Data/RDS_Objects/Selection_Gradients_Knivsasen_2022.rds")))
  
data_selection_gradients_veberod_2022 <- read_rds(paste0(here::here("Data/RDS_Objects/Selection_Gradients_Veberod_2022.rds")))
```

```{r}
data_selection_gradients <- rbind(data_selection_gradients_knivsasen_2021,
                                  data_selection_gradients_knivsasen_2022,
                                  data_selection_gradients_veberod_2022)
```

# Graph: Mean-Standardized Phenotypic Selection Gradients (Knivsåsen 2021, Knivsåsen 2022, Veberöd 2022)

```{r}
labels_columns <- c("Stem_Height" = "Inflorescence\nLength (IL)",
                    "Stickidium" = "Glandular Region\nLength (GR)",
                    "Corolla_Diameter" = "Corolla\nDiameter (CD)",
                    "Tube_Width" = "Floral Tube\nWidth (TW)",
                    "Tube_Length" = "Floral Tube\nLength (TL)",
                    "NSD" = "Nectary-Stigma\nDistance (NSD)",
                    "Total_Flowers" = "Number of\nFlowers (FN)")
```

```{r}
compare_observational <-data.frame(Trait = c("Stickidium", "Total_Flowers", "Stickidium", "Corolla_Diameter", "NSD"),
                                   .y. = c("Mean_Selection_Gradient", "Mean_Selection_Gradient", "Mean_Selection_Gradient", "Mean_Selection_Gradient", "Mean_Selection_Gradient"),
                                   group1 = c("Knivsasen_2022", "Knivsasen_2022", "Knivsasen_2021", "Knivsasen_2021", "Knivsasen_2021"),
                                   group2 = c("Veberod_2022", "Veberod_2022", "Knivsasen_2022", "Veberod_2022", "Veberod_2022"),
                                   p.adj = c("*", I("\u2020"), "*", I("\u2020"), I("\u2020")))
```

```{r}
tiff(paste0(here::here("Selection_Gradients_Observational.tiff")), units = "in", width = 10.5, height = 5, res = 300)
data_selection_gradients %>% 
  filter(Treatment %in% c("Open_Control")) %>% 
  mutate(Trait = factor(Trait, levels = c("Stem_Height", "Stickidium", "Total_Flowers", "Corolla_Diameter", "Tube_Width", "Tube_Length", "NSD"))) %>% 
  ggbarplot(x = "Population",
            y = "Mean_Selection_Gradient",
            fill = "Population",
            alpha = 0.75,
            facet.by = "Trait",
            nrow = 1,
            color = "black") +
  geom_errorbar(aes(ymin = Mean_Selection_Gradient - Mean_SE_Selection_Gradient,
                    ymax = Mean_Selection_Gradient + Mean_SE_Selection_Gradient),
                position = position_dodge(), width = 0.1) +
  geom_point(data = data.frame(Population = 2, Mean_Selection_Gradient = 0.273, Trait = "Stem_Height"), size = 2.5, color="red") +
  geom_point(data = data.frame(Population = 2, Mean_Selection_Gradient = 0.105, Trait = "Stickidium"), size = 2.5, color="red") +
  geom_point(data = data.frame(Population = 2, Mean_Selection_Gradient = 0.939, Trait = "Total_Flowers"), size = 2.5, color="red") +
  geom_point(data = data.frame(Population = 2, Mean_Selection_Gradient = 0.397, Trait = "Corolla_Diameter"), size = 2.5, color="red") +
  geom_point(data = data.frame(Population = 2, Mean_Selection_Gradient = 0.141, Trait = "Tube_Width"), size = 2.5, color="red") +
  geom_point(data = data.frame(Population = 2, Mean_Selection_Gradient = 0.087, Trait = "Tube_Length"), size = 2.5, color="red") +
  geom_point(data = data.frame(Population = 2, Mean_Selection_Gradient = 0.118, Trait = "NSD"), size = 2.5, color="red") +
  theme_bw(base_size = 15) +
  xlab("Population") +
  ylab(expression(paste("Mean-Standardized Selection Gradient (", beta, ")"))) +
  geom_hline(yintercept = 0, linetype = "solid") +
  facet_grid(cols = vars(Trait = factor(Trait, levels = c("Stem_Height", "Stickidium", "Total_Flowers", "Corolla_Diameter", "Tube_Width", "Tube_Length", "NSD"))),
             labeller = labeller(Trait = as_labeller(labels_columns))) +
  theme(legend.position = "top",
        legend.title = element_blank(),
        axis.text.x = element_text(size = 15, angle = 90),
        axis.text.y = element_text(size = 15),
        panel.grid.minor = element_blank()) +
  scale_fill_grey(start = 0.95, end = 0.05,
                  labels = c(expression(paste("Knivsåsen 2021 (K"[2021], ")")),
                             expression(paste("Knivsåsen 2022 (K"[2022], ")")),
                             expression(paste("Veberöds Ljung 2022 (V"[2022], ")")))) +
  scale_y_continuous(limits = c(-1.2, 1.5), breaks = seq(-1, 1.5, by = 0.5)) +
  geom_text(mapping = aes(x = Population, y = Mean_Selection_Gradient / 1000, label = Significant),
            position = position_dodgenudge(y = -0.1, x = 0, direction = "split", width = 1),
            size = 5) +
  # stat_pvalue_manual(compare_observational, y.position = 1.5, size = 5) +
  scale_x_discrete(labels = c(expression(paste("K"[2021])),
                              expression(paste("K"[2022])),
                              expression(paste("V"[2022]))))
```

# Graph: Mean-Standardized Phenotypic Selection Gradients (Temporal Pollinator Exclussion Experiment)

## No Exclusion of Pollinators (NO) vs. Complete Exclusion of Pollinators (CE)

```{r}
compare_CE_NO <-data.frame(Trait = c("Tube_Width", "Total_Flowers"),
                           .y. = c("Mean_Selection_Gradient", "Mean_Selection_Gradient"),
                           group1 = c("Open_Control", "Open_Control"),
                           group2 = c("Always_Caged", "Always_Caged"),
                           p.adj = c("**",I("\u2020")))
```

```{r message=FALSE}
graph_selection_gradients_CE_NO <-
data_selection_gradients %>% 
  filter(Population == "Veberod_2022") %>% 
  filter(Treatment %in% c("Open_Control", "Always_Caged")) %>% 
  mutate(Treatment = factor(Treatment, levels = c("Always_Caged", "Open_Control"))) %>% 
  mutate(Trait = factor(Trait, levels = c("Stem_Height", "Stickidium", "Total_Flowers", "Corolla_Diameter", "Tube_Width", "Tube_Length", "NSD"))) %>% 
  ggbarplot(x = "Treatment",
            y = "Mean_Selection_Gradient",
            fill = "Treatment",
            palette = c("#D55E00", "#009E73"),
            alpha = 0.5,
            facet.by = "Trait",
            nrow = 1,
            color = "black") +
  geom_text(mapping = aes(x = Treatment, y = Mean_Selection_Gradient / 1000, label = Significant),
            position = position_dodgenudge(y = -0.5, x = 0, direction = "split", width = 1),
            size = 5) +
  geom_errorbar(aes(ymin = Mean_Selection_Gradient - Mean_SE_Selection_Gradient,
                    ymax = Mean_Selection_Gradient + Mean_SE_Selection_Gradient),
                position = position_dodge(), width = 0.1) +
  theme_bw(base_size = 15) +
  xlab("Experimental Treatment") +
  ylab(expression(paste("Mean-Standardized Selection Gradient (", beta, ")"))) +
  geom_hline(yintercept = 0, linetype = "solid") +
  theme(legend.position = "top",
        legend.title = element_blank(),
        legend.text = element_text(size = 15),
        axis.text.x = element_text(size = 15),
        axis.text.y = element_text(size = 15),
        panel.grid.minor = element_blank()) +
  scale_fill_manual(values = c("#D55E00", "#009E73"),
                    labels = c("Complete Exclusion of Pollinators (CE)", "No Exclusion of Pollinators (NO)")) +
  scale_y_continuous(limits = c(-3.25, 4.5), breaks = seq(-3, 4, by = 1)) +
  scale_x_discrete(labels = c("CE", "NO")) +
  facet_grid(cols = vars(Trait = factor(Trait,levels = c("Stem_Height", "Stickidium", "Total_Flowers", "Corolla_Diameter", "Tube_Width", "Tube_Length", "NSD"))),
             labeller = labeller(Trait = as_labeller(labels_columns)))
  # stat_pvalue_manual(compare_CE_NO, y.position = 4.75, size = 5)
```

# Exclusion of Diurnal Pollinators (DE) vs. Exclusion of Nocturnal Pollinators (NE)

```{r}
compare_DE_NE <-data.frame(Trait = "Stickidium",
                           .y. = "Mean_Selection_Gradient",
                           group1 = "Day_Caged",
                           group2 = "Night_Caged",
                           p.adj = I("\u2020"))
```

```{r message=FALSE}
graph_selection_gradients_DE_NE <-
data_selection_gradients %>% 
  filter(Population == "Veberod_2022") %>% 
  filter(Treatment %in% c("Day_Caged", "Night_Caged")) %>% 
  mutate(Trait = factor(Trait, levels = c("Stem_Height", "Stickidium", "Total_Flowers", "Corolla_Diameter", "Tube_Width", "Tube_Length", "NSD"))) %>%
  ggbarplot(x = "Treatment",
            y = "Mean_Selection_Gradient",
            fill = "Treatment",
            palette = c("#999999", "#F0E442"),
            alpha = 0.5,
            facet.by = "Trait",
            nrow = 1,
            color = "black") +
  geom_text(mapping = aes(x = Treatment, y = Mean_Selection_Gradient / 1000, label = Significant),
            position = position_dodgenudge(y = -0.5, x = 0, direction = "split", width = 1),
            size = 5) +
  geom_errorbar(aes(ymin = Mean_Selection_Gradient - Mean_SE_Selection_Gradient,
                    ymax = Mean_Selection_Gradient + Mean_SE_Selection_Gradient),
                position = position_dodge(), width = 0.1) +
  theme_bw(base_size = 15) +
  xlab("Experimental Treatment") +
  ylab(expression(paste("Mean-Standardized Selection Gradient (", beta, ")"))) +
  geom_hline(yintercept = 0, linetype = "solid") +
  theme(legend.position = "top",
        legend.title = element_blank(),
        legend.text = element_text(size = 15),
        axis.text.x = element_text(size = 15),
        axis.text.y = element_text(size = 15),
        panel.grid.minor = element_blank()) +
  scale_fill_manual(values = c("#999999", "#F0E442"),
                    labels = c("Exclusion of Diurnal Pollinators (DE)", "Exclusion of Nocturnal Pollinators (NE)")) +
  scale_y_continuous(limits = c(-3.25, 4.5), breaks = seq(-3, 4, by = 1)) +
  scale_x_discrete(labels = c("DE", "NE")) +
  facet_grid(cols = vars(Trait = factor(Trait,levels = c("Stem_Height", "Stickidium", "Total_Flowers", "Corolla_Diameter", "Tube_Width", "Tube_Length", "NSD"))),
             labeller = labeller(Trait = as_labeller(labels_columns)))
  # stat_pvalue_manual(compare_DE_NE, y.position = 4.75, size = 5)
```

## Assemble Graph for Temporal Pollinator Exclusion

```{r}
tiff(paste0(here::here("Selection_Gradients_Experiment.tiff")), units = "in", width = 10.5, height = 10.5, res = 300)
ggarrange(graph_selection_gradients_CE_NO, graph_selection_gradients_DE_NE,
          labels = c("(A)", "(B)"),
          ncol = 1,
          common.legend = FALSE, legend = "top")
```

# Divergence in Phenotypic Selecion on Floral Traits

```{r}
data_selection_gradients_difference <- read_rds(paste0(here::here("Data/RDS_Objects/Data_Selection_Gradients_Difference.rds")))
```

```{r}
data_selection_gradients_difference <- data_selection_gradients_difference %>% 
  mutate(Difference_Corrected = replace_na(Difference_Corrected, 0))
```

```{r}
data_selection_gradients_difference <- data_selection_gradients_difference %>% 
  pivot_longer(cols = c("Difference", "Difference_Corrected"),
               names_to = "Type",
               values_to = "Difference_Value")
```

```{r}
data_selection_gradients_difference <- data_selection_gradients_difference %>% 
  mutate(SE = ifelse(Type == "Difference_Corrected", NA, SE))
```

```{r}
tiff(paste0(here::here("Selection_Gradients_Difference_Corrected.tiff")), units = "in", width = 10.5, height = 5, res = 300)
data_selection_gradients_difference %>% 
  mutate(Trait = factor(Trait, levels = c("Stem_Height", "Stickidium", "Total_Flowers", "Corolla_Diameter", "Tube_Width", "Tube_Length", "NSD"))) %>% 
  ggplot(aes(x = Pollinator_Divergence, y = Difference_Value)) +
  geom_hline(yintercept = 0, linetype = "solid") +
  geom_line(aes(group = Type, color = Type), linewidth = 1) +
  geom_point(data = . %>% filter(Type == "Difference"), aes(color = Type, group = Type), size = 3) +
  geom_errorbar(aes(ymin = Difference_Value - SE, ymax = Difference_Value + SE), position = position_dodge(), width = 0.2) +
  geom_point(data = . %>% filter(Type == "Difference_Corrected"), aes(color = Type, group = Type), size = 3) +
  theme_bw(base_size = 12) +
  xlab("Divergence in Local Pollinator Assemblage") +
  # ylab(bquote(atop("Absolute Value of Difference in", "Phenotypic Selection Gradients (|" ~ beta[i] ~ " - " ~ beta[j] ~ "|)"))) +
  ylab(bquote(atop("Absolute Value of Difference in", "Phenotypic Selection Gradients (" ~ italic("D") ~ ")"))) +
  facet_wrap(~ Trait,
             nrow = 1,
             labeller = labeller(Trait = as_labeller(labels_columns))) +
  theme(legend.position = "none",
        legend.title = element_blank(),
        panel.grid.minor = element_blank(),
        axis.text.x = element_text(angle = 90, size = 10, hjust = 1, vjust = 0.375),
        axis.text.y = element_text(size = 12),
        axis.title.y.right = element_text(color = "darkgray"),
        axis.text.y.right = element_text(color = "darkgray"),
        axis.ticks.y.right = element_line(color = "darkgray")) +
  scale_x_discrete(limits = c("Low", "Mid", "High"),
                   labels = c(expression(atop(NA, atop(textstyle("Temporal: "), textstyle("K"[2021] * " - K"[2022])))),
                              expression(atop(NA, atop(textstyle("Spatial: "), textstyle("K"[2022] * " - V"[2022])))),
                              expression(atop(NA, atop(textstyle("Experimental: "), textstyle("V"[DE] * " - V"[NE])))))) +
  scale_y_continuous(sec.axis = sec_axis(~ ., name = expression(atop("Error-Corrected Difference in", paste("Phenotypic Selection Gradients (" ~ italic(D[C]) ~ ")"))))) +
  scale_color_manual(values = c("Difference" = "black", "Difference_Corrected" = "gray"))
```

# Load Data: Mean-Standardized Phenotypic Selection Gradients at the Plant Level

```{r}
data_selection_gradients_plant_level <- read_rds(paste0(here::here("Data/RDS_Objects/Selection_Gradients_Plant_Level.rds")))
```

```{r}
tiff(paste0(here::here("Selection_Gradients_Observational_Plant_Level.tiff")), units = "in", width = 10.5, height = 5, res = 300)
data_selection_gradients_plant_level %>% 
  filter(Treatment == "Open_Control") %>% 
  mutate(Trait = factor(Trait, levels = c("Stem_Height", "Stickidium", "Total_Flowers", "Corolla_Diameter", "Tube_Width", "Tube_Length", "NSD"))) %>% 
  ggbarplot(x = "Population",
            y = "Mean_Selection_Gradient",
            fill = "Population",
            alpha = 0.75,
            facet.by = "Trait",
            nrow = 1,
            color = "black") +
  geom_errorbar(aes(ymin = Mean_Selection_Gradient - Mean_SE_Selection_Gradient,
                    ymax = Mean_Selection_Gradient + Mean_SE_Selection_Gradient),
                position = position_dodge(), width = 0.1) +
  theme_bw(base_size = 15) +
  xlab("Population") +
  ylab(expression(paste("Mean-Standardized Selection Gradient (", beta, ")"))) +
  geom_hline(yintercept = 0, linetype = "solid") +
  facet_grid(cols = vars(Trait = factor(Trait, levels = c("Stem_Height", "Stickidium", "Total_Flowers", "Corolla_Diameter", "Tube_Width", "Tube_Length", "NSD"))),
             labeller = labeller(Trait = as_labeller(labels_columns))) +
  theme(legend.position = "top",
        legend.title = element_blank(),
        axis.text.x = element_text(size = 15, angle = 90),
        axis.text.y = element_text(size = 15),
        panel.grid.minor = element_blank()) +
  scale_fill_grey(start = 0.95, end = 0.05,
                  labels = c(expression(paste("Knivsåsen 2021 (K"[2021], ")")),
                             expression(paste("Knivsåsen 2022 (K"[2022], ")")),
                             expression(paste("Veberöds Ljung 2022 (V"[2022], ")")))) +
  scale_y_continuous(limits = c(-1.2, 2), breaks = seq(-1, 2, by = 0.5)) +
  geom_text(mapping = aes(x = Population, y = Mean_Selection_Gradient / 1000, label = Significant),
            position = position_dodgenudge(y = -0.1, x = 0, direction = "split", width = 1),
            size = 5) +
  scale_x_discrete(labels = c(expression(paste("K"[2021])),
                              expression(paste("K"[2022])),
                              expression(paste("V"[2022]))))
```

# Load Data: Mean Value and Error-Corrected Variance of the Mean-Standardized Phenotypic Selection Gradients

```{r}
data_selection_gradients_mean_variance_K21_K22_V22 <- read_rds(paste0(here::here("Data/RDS_Objects/Selection_Gradients_Error_Corrected.rds")))
```

```{r}
data_selection_gradients_mean_variance_experiment <- read_rds(paste0(here::here("Data/RDS_Objects/Selection_Gradients_Error_Corrected_Experiment.rds")))
```

```{r}
data_selection_gradients_mean_variance <- rbind(data_selection_gradients_mean_variance_K21_K22_V22,
                                                data_selection_gradients_mean_variance_experiment)
```

```{r}
data_selection_gradients_mean_variance <- data_selection_gradients_mean_variance %>% 
  mutate(Varriance_Corrected_Mean_Selection_Gradient = replace_na(Varriance_Corrected_Mean_Selection_Gradient, 0))
```

```{r}
data_selection_gradients_mean_variance %>% 
  mutate(Trait = factor(Trait, levels = c("Stem_Height", "Stickidium", "Total_Flowers", "Corolla_Diameter", "Tube_Width", "Tube_Length", "NSD"))) %>% 
  ggplot(aes(y = Varriance_Corrected_Mean_Selection_Gradient, x = Trait, group = Comparison)) +
  geom_point(aes(shape = Comparison, color = Comparison), size = 5, stroke = 2.5) +
  scale_x_discrete(labels = c("Inflorescence\nLength (IL)",
                              "Glandular Region\nLength (GR)",
                              "Number of\nFlowers (FN)",
                              "Corolla\nDiameter (CD)",
                              "Floral Tube\nWidth (TW)",
                              "Floral Tube\nLength (TL)",
                              "Nectary-Stigma\nDistance (NSD)")) +
  scale_color_manual(values = c("blue", "cyan", "green", "orange", "red"),
                     breaks = c("Temporal", "Spatial", "Spatial_Temporal", "NO_CE", "DE_NE"),
                     labels = c(expression(paste("Temporal:", "K"[2021], "- K"[2022])),
                                expression(paste("Spatial:", "K"[2022], " - V"[2022])),
                                expression(paste("Spatial and Temporal: K"[2021], " - V"[2022])),
                                "Complete Exclusion of Pollinators (CE)\nNo Exclusion of Pollinators (NO)",
                                "Exclusion of Diurnal Pollinators (DE)\nExclusion of Nocturnal Pollinators (NE)")) +
  scale_shape_manual(values = c(21, 22, 23, 24, 25),
                     breaks = c("Temporal", "Spatial", "Spatial_Temporal", "NO_CE", "DE_NE"),
                     labels = c(expression(paste("Temporal:", "K"[2021], "- K"[2022])),
                                expression(paste("Spatial:", "K"[2022], " - V"[2022])),
                                expression(paste("Spatial and Temporal: K"[2021], " - V"[2022])),
                                "Complete Exclusion of Pollinators (CE)\nNo Exclusion of Pollinators (NO)",
                                "Exclusion of Diurnal Pollinators (DE)\nExclusion of Nocturnal Pollinators (NE)")) +
  theme_bw(base_size = 15) +
  xlab("Floral Trait") +
  ylab(expression(atop("Error-Corrected Standard Deviation of", paste("Mean-Standardized Selection Gradient (", sigma[beta]^c, ")")))) +
  theme(legend.position = "right",
        legend.title = element_blank(),
        legend.text = element_text(size = 15),
        legend.text.align = 0,
        legend.key.height = unit(1.5, "cm"),
        axis.text.x = element_text(size = 15, angle = 90),
        axis.text.y = element_text(size = 15),
        panel.grid.minor = element_blank())
```

```{r}
data_selection_gradients_difference_mean_variance <- rbind(data_selection_gradients_difference %>% 
                                                             rename(Value = Difference) %>% 
                                                             mutate(Type = "Absolute_Difference") %>% 
                                                             select(Trait, Value, SE, Comparison, Type),
                                                           data_selection_gradients_mean_variance %>% 
                                                             mutate(SE = NA) %>% 
                                                             rename(Value = Varriance_Corrected_Mean_Selection_Gradient) %>% 
                                                             mutate(Type = "Error_Corrected_Variance") %>% 
                                                             select(Trait, Value, SE, Comparison, Type))
```

```{r}
data_selection_gradients_difference_mean_variance <- data_selection_gradients_difference_mean_variance %>% 
  mutate(Comparison = str_replace(Comparison, "KN_21_KN_22", "Temporal")) %>% 
  mutate(Comparison = str_replace(Comparison, "KN_22_VB_22", "Spatial")) %>% 
  mutate(Comparison = str_replace(Comparison, "Day_Exclusion_Night_Exclusion", "DE_NE"))
```

```{r}
tiff(paste0(here::here("Selection_Gradients_Difference_Variance.tiff")), units = "in", width = 10.5, height = 5, res = 300)
data_selection_gradients_difference_mean_variance %>% 
  filter(Comparison %in% c("Temporal", "Spatial", "DE_NE")) %>% 
  mutate(Trait = factor(Trait, levels = c("Stem_Height", "Stickidium", "Total_Flowers", "Corolla_Diameter", "Tube_Width", "Tube_Length", "NSD"))) %>% 
  mutate(Type = factor(Type, levels = c("Absolute_Difference", "Error_Corrected_Variance"))) %>% 
  ggplot(aes(x = Comparison, y = Value)) +
  geom_hline(yintercept = 0, linetype = "solid") +
  geom_line(aes(group = Type, color = Type), linewidth = 1) +
  geom_point(data = . %>% filter(Type == "Error_Corrected_Variance"), aes(color = Type, group = Type), size = 3) +
  geom_point(data = . %>% filter(Type == "Absolute_Difference"), aes(color = Type, group = Type), size = 3) +
  theme_bw(base_size = 12) +
  xlab("Source of Variation") +
  ylab(bquote(atop("Absolute Value of Difference in", "Phenotypic Selection Gradients (|" ~ beta[i] ~ " - " ~ beta[j] ~ "|)"))) +
  facet_wrap(~ Trait, nrow = 1, labeller = labeller(Trait = as_labeller(labels_columns))) +
  theme(legend.position = "none",
        legend.title = element_blank(),
        panel.grid.minor = element_blank(),
        axis.text.x = element_text(angle = 90, size = 10, hjust = 1, vjust = 0.375),
        axis.text.y = element_text(size = 12),
        axis.title.y.right = element_text(color = "darkgray"),
        axis.text.y.right = element_text(color = "darkgray"),
        axis.ticks.y.right = element_line(color = "darkgray")) +
  scale_x_discrete(limits = c("Temporal", "Spatial", "DE_NE"),
                   labels = c(expression(atop(NA, atop(textstyle("Temporal: "), textstyle("K"[2021] * " - K"[2022])))),
                              expression(atop(NA, atop(textstyle("Spatial: "), textstyle("K"[2022] * " - V"[2022])))),
                              expression(atop(NA, atop(textstyle("Experimental: "), textstyle("V"[DE] * " - V"[NE])))))) +
  scale_y_continuous(limits = c(-1, 3.75),
                     breaks = seq(-1, 3.75, by = 1),
                     sec.axis = sec_axis(~.,
                                         name = expression(atop("Error-Corrected Standard Deviation of", paste("Mean-Standardized Selection Gradient (", sigma[beta]^c, ")"))))) +
  geom_errorbar(aes(ymin = Value - SE, ymax = Value + SE), position = position_dodge(), width = 0.2) +
  scale_color_manual(values = c("Absolute_Difference" = "black", "Error_Corrected_Variance" = "gray"))
```

```{r}
data_selection_gradients_mean_variance_spatio_temporal <- read_rds(paste0(here::here("Data/RDS_Objects/Selection_Gradients_Error_Corrected_Spatio_Temporal.rds")))
```

```{r}
data_selection_gradients_mean_variance_spatio_temporal <- data_selection_gradients_mean_variance_spatio_temporal %>% 
  mutate(Varriance_Corrected_Mean_Selection_Gradient = replace_na(Varriance_Corrected_Mean_Selection_Gradient, 0))
```

```{r}
tiff(paste0(here::here("Selection_Gradients_Difference_Variance_Spatio_Temporal.tiff")), units = "in", width = 11.5, height = 7, res = 300)
data_selection_gradients_mean_variance_spatio_temporal %>% 
  mutate(Trait = factor(Trait, levels = c("Stem_Height", "Total_Flowers", "Corolla_Diameter", "Tube_Width", "Tube_Length", "NSD", "Stickidium"))) %>% 
  ggplot(aes(x = Trait, y = Varriance_Corrected_Mean_Selection_Gradient)) +
  geom_bar(stat = "identity", color = "black", fill = "black", alpha = 0.75) +
  theme_bw(base_size = 15) +
  xlab("") +
  ylab(expression(atop("Error-Corrected Standard Deviation of", paste("Mean-Standardized Selection Gradient (", sigma[beta]^c, ")")))) +
  theme(legend.position = "none",
        legend.title = element_blank(),
        panel.grid.minor = element_blank(),
        axis.text.x = element_text(angle = 90, hjust = 1, vjust = 0.5, size = 15),
        axis.text.y = element_text(size = 15)) +
  scale_x_discrete(limits = c("Stem_Height", "Total_Flowers", "Corolla_Diameter", "Tube_Width", "Tube_Length", "NSD", "Stickidium"),
                   labels = c("Inflorescence\nLength (IL)",
                              "Number of\nFlowers (FN)",
                              "Corolla\nDiameter (CD)",
                              "Floral Tube\nWidth (TW)",
                              "Floral Tube\nLength (TL)",
                              "Nectary-Stigma\nDistance (NSD)",
                              "Glandular Region\nLength (GR)")) +
  scale_y_continuous(limits = c(0, 0.4),
                     breaks = seq(0, 0.4, by = 0.1))
```