---
title: "Phenotypic Selection on Floral Traits: Knivs책sen 2022"
---

```{r include=FALSE}
library(readxl)
library(dplyr)
library(ggplot2)
library(nlme)
library(reshape2)
library(MuMIn)
library(performance)
```

# Load Data: Knivs책sen 2022

```{r}
data_knivsasen_2022 <- readxl::read_excel(paste0(here::here("Data/Raw_Data/Selection_2022_15-02-23.xlsx")), sheet = "Knivsasen_2022")
```

```{r}
data_knivsasen_2022 <- suppressWarnings(data_knivsasen_2022 %>% 
                                          mutate_at(c("Capsules_Collected",
                                                      "Seeds_Weight",
                                                      "Stem_Height",
                                                      "Flowers_First_Visit",
                                                      "Buds_First_Visit",
                                                      "Eaten_Buds_First_Visit",
                                                      "Capsules_First_Visit",
                                                      "Corolla_Diameter",
                                                      "Tube_Width",
                                                      "Tube_Length",
                                                      "NSD",
                                                      "Stickidium",
                                                      "Open_Capsules_Second_Visit",
                                                      "Closed_Capsules_Second_Visit",
                                                      "Eaten_Capsules_Second_Visit",
                                                      "Failed_Flowers_Second_Visit",
                                                      "Flowers_Second_Visit",
                                                      "Buds_Second_Visit"),
                                                    as.numeric))
```

# Plant Reproductive Success: Knivs책sen 2022

```{r}
data_knivsasen_2022 <- data_knivsasen_2022 %>% 
  mutate(Total_Flowers = 
           Open_Capsules_Second_Visit + 
           Closed_Capsules_Second_Visit + 
           Eaten_Capsules_Second_Visit + 
           Failed_Flowers_Second_Visit + 
           Flowers_Second_Visit +
           Buds_Second_Visit) %>% 
  mutate(Total_Fruits = 
           Open_Capsules_Second_Visit + 
           Closed_Capsules_Second_Visit + 
           Eaten_Capsules_Second_Visit) %>% 
  mutate(Mean_Seeds_Weight = round(Seeds_Weight / Capsules_Collected, digits = 4)) %>% 
  mutate(Fruit_Yield_Total_Fruits = Total_Fruits * Mean_Seeds_Weight)
```

```{r}
data_knivsasen_2022 <- data_knivsasen_2022 %>% 
  mutate(Relative_Total_Flowers = round(Total_Flowers / mean(Total_Flowers, na.rm = TRUE), digits = 4)) %>% 
  mutate(Relative_Total_Fruits = round(Total_Fruits / mean(Total_Fruits, na.rm = TRUE), digits = 4)) %>% 
  mutate(Relative_Mean_Seeds_Weight = round(Mean_Seeds_Weight / mean(Mean_Seeds_Weight, na.rm = TRUE), digits = 4)) %>% 
  mutate(Relative_Fruit_Yield_Total_Fruits = round(Fruit_Yield_Total_Fruits / mean(Fruit_Yield_Total_Fruits, na.rm = TRUE), digits = 4))
```

# Mean Centre Predictor Variables

```{r}
data_knivsasen_2022 <- data_knivsasen_2022 %>% 
  mutate(Stem_Height_Mean_Centred = scale(Stem_Height, scale = FALSE)) %>% 
  mutate(Corolla_Diameter_Mean_Centred = scale(Corolla_Diameter, scale = FALSE)) %>% 
  mutate(Tube_Width_Mean_Centred = scale(Tube_Width, scale = FALSE)) %>% 
  mutate(Tube_Length_Mean_Centred = scale(Tube_Length, scale = FALSE)) %>% 
  mutate(NSD_Mean_Centred = scale(NSD, scale = FALSE)) %>% 
  mutate(Stickidium_Mean_Centred = scale(Stickidium, scale = FALSE)) %>% 
  mutate(Total_Flowers_Mean_Centred = scale(Total_Flowers, scale = FALSE))
```

```{r}
saveRDS(data_knivsasen_2022, 
        file = paste0(here::here("Data/RDS_Objects/Data_Phenotypes_Knivsasen_2022.rds")))
```

# Linear Mixed-Effects Models

## Directional Phenotypic Selection

```{r}
data_knivsasen_2022_selection_models_linear <- nlme::lme(Relative_Fruit_Yield_Total_Fruits ~
                                                           Stem_Height_Mean_Centred +
                                                           Corolla_Diameter_Mean_Centred + 
                                                           Tube_Width_Mean_Centred +
                                                           Tube_Length_Mean_Centred +
                                                           NSD_Mean_Centred +
                                                           Stickidium_Mean_Centred +
                                                           Total_Flowers_Mean_Centred,
                                                         random = ~ 1 | Plant_ID,
                                                         na.action = na.omit,
                                                         data = data_knivsasen_2022)
```

## Quadratic and Correlational Phenotypic Selection

```{r}
data_knivsasen_2022_selection_models_quadratic <- nlme::lme(Relative_Fruit_Yield_Total_Fruits ~
                                                              Stem_Height_Mean_Centred +
                                                              Corolla_Diameter_Mean_Centred + 
                                                              Tube_Width_Mean_Centred +
                                                              Tube_Length_Mean_Centred +
                                                              NSD_Mean_Centred +
                                                              Stickidium_Mean_Centred +
                                                              Total_Flowers_Mean_Centred +
                                                              I(Stem_Height_Mean_Centred^2) +
                                                              I(Corolla_Diameter_Mean_Centred^2) +
                                                              I(Tube_Width_Mean_Centred^2) +
                                                              I(Tube_Length_Mean_Centred^2) +
                                                              I(NSD_Mean_Centred^2) +
                                                              I(Stickidium_Mean_Centred^2) +
                                                              I(Total_Flowers_Mean_Centred^2) +
                                                              Stem_Height_Mean_Centred:Corolla_Diameter_Mean_Centred +
                                                              Stem_Height_Mean_Centred:Tube_Width_Mean_Centred +
                                                              Stem_Height_Mean_Centred:Tube_Length_Mean_Centred +
                                                              Stem_Height_Mean_Centred:NSD_Mean_Centred +
                                                              Stem_Height_Mean_Centred:Stickidium_Mean_Centred +
                                                              Stem_Height_Mean_Centred:Total_Flowers_Mean_Centred +
                                                              Corolla_Diameter_Mean_Centred:Tube_Width_Mean_Centred +
                                                              Corolla_Diameter_Mean_Centred:Tube_Length_Mean_Centred +
                                                              Corolla_Diameter_Mean_Centred:NSD_Mean_Centred +
                                                              Corolla_Diameter_Mean_Centred:Stickidium_Mean_Centred +
                                                              Corolla_Diameter_Mean_Centred:Total_Flowers_Mean_Centred +
                                                              Tube_Width_Mean_Centred:Tube_Length_Mean_Centred +
                                                              Tube_Width_Mean_Centred:NSD_Mean_Centred +
                                                              Tube_Width_Mean_Centred:Stickidium_Mean_Centred +
                                                              Tube_Width_Mean_Centred:Total_Flowers_Mean_Centred +
                                                              Tube_Length_Mean_Centred:NSD_Mean_Centred +
                                                              Tube_Length_Mean_Centred:Stickidium_Mean_Centred +
                                                              Tube_Length_Mean_Centred:Total_Flowers_Mean_Centred +
                                                              NSD_Mean_Centred:Stickidium_Mean_Centred +
                                                              NSD_Mean_Centred:Total_Flowers_Mean_Centred +
                                                              Stickidium_Mean_Centred:Total_Flowers_Mean_Centred,
                                                            random = ~ 1 | Plant_ID,
                                                            na.action = na.omit,
                                                            data = data_knivsasen_2022)
```

## Compare Performance: Directional, Quadratic, and Correlational Phenotypic Selection

```{r}
data_knivsasen_2022_models_performance <- compare_performance(data_knivsasen_2022_selection_models_linear,
                                                              data_knivsasen_2022_selection_models_quadratic,
                                                              metrics = c("AIC", "R2"), estimator = "ML")
```

# Mean and Standard Deviation of Floral Traits: Knivs책sen 2022

```{r}
data_knivsasen_2022_mean_traits <- data_knivsasen_2022 %>% 
  summarise_at(c("Stem_Height",
                 "Corolla_Diameter",
                 "Tube_Width",
                 "Tube_Length",
                 "NSD",
                 "Stickidium",
                 "Total_Flowers"),
               mean, na.rm = TRUE)
```

```{r message=FALSE}
data_knivsasen_2022_mean_traits <- melt(data_knivsasen_2022_mean_traits, value.name = "Trait_Mean", variable.name = "Trait")
```

```{r}
data_knivsasen_2022_sd_traits <- data_knivsasen_2022 %>% 
  summarise_at(c("Stem_Height",
                 "Corolla_Diameter",
                 "Tube_Width",
                 "Tube_Length",
                 "NSD",
                 "Stickidium",
                 "Total_Flowers"),
               sd, na.rm = TRUE)
```

```{r message=FALSE}
data_knivsasen_2022_sd_traits <- melt(data_knivsasen_2022_sd_traits, value.name = "Trait_SD", variable.name = "Trait")
```

```{r}
data_knivsasen_2022_summary_traits <- left_join(data_knivsasen_2022_mean_traits,
                                                data_knivsasen_2022_sd_traits,
                                                by = c("Trait" = "Trait"))
```

```{r}
data_knivsasen_2022_summary_traits <- data_knivsasen_2022_summary_traits %>% 
  mutate_if(is.numeric,
            round,
            digits = 4)
```

# Mean-Standardized Phenotypic Selection Gradients

```{r}
data_knivsasen_2022_selection_gradients <-
  data.frame(Trait = c("Stem_Height",
                       "Corolla_Diameter",
                       "Tube_Width",
                       "Tube_Length",
                       "NSD",
                       "Stickidium",
                       "Total_Flowers"),
             Method = rep(c("Linear"), each = 7),
             Estimate = c(data_knivsasen_2022_selection_models_linear$coefficients$fixed[[2]],
                          data_knivsasen_2022_selection_models_linear$coefficients$fixed[[3]],
                          data_knivsasen_2022_selection_models_linear$coefficients$fixed[[4]],
                          data_knivsasen_2022_selection_models_linear$coefficients$fixed[[5]],
                          data_knivsasen_2022_selection_models_linear$coefficients$fixed[[6]],
                          data_knivsasen_2022_selection_models_linear$coefficients$fixed[[7]],
                          data_knivsasen_2022_selection_models_linear$coefficients$fixed[[8]]),
             SE_Model = c(sqrt(diag(vcov(data_knivsasen_2022_selection_models_linear))[[2]]),
                          sqrt(diag(vcov(data_knivsasen_2022_selection_models_linear))[[3]]),
                          sqrt(diag(vcov(data_knivsasen_2022_selection_models_linear))[[4]]),
                          sqrt(diag(vcov(data_knivsasen_2022_selection_models_linear))[[5]]),
                          sqrt(diag(vcov(data_knivsasen_2022_selection_models_linear))[[6]]),
                          sqrt(diag(vcov(data_knivsasen_2022_selection_models_linear))[[7]]),
                          sqrt(diag(vcov(data_knivsasen_2022_selection_models_linear))[[8]])),
             p = c(summary(data_knivsasen_2022_selection_models_linear)$tTable[,"p-value"][[2]],
                   summary(data_knivsasen_2022_selection_models_linear)$tTable[,"p-value"][[3]],
                   summary(data_knivsasen_2022_selection_models_linear)$tTable[,"p-value"][[4]],
                   summary(data_knivsasen_2022_selection_models_linear)$tTable[,"p-value"][[5]],
                   summary(data_knivsasen_2022_selection_models_linear)$tTable[,"p-value"][[6]],
                   summary(data_knivsasen_2022_selection_models_linear)$tTable[,"p-value"][[7]],
                   summary(data_knivsasen_2022_selection_models_linear)$tTable[,"p-value"][[8]]))
```

```{r}
data_knivsasen_2022_selection_gradients <- data_knivsasen_2022_selection_gradients %>% 
  mutate_if(is.numeric,
            round,
            digits = 4)
```

```{r}
data_knivsasen_2022_selection_gradients <- data_knivsasen_2022_selection_gradients %>% 
  mutate(Significant = ifelse(p >= 0.05 & p <= 0.10, paste0(expression("\u2020")),
                              ifelse(data_knivsasen_2022_selection_gradients$p < 0.05 & data_knivsasen_2022_selection_gradients$p > 0.01, "*",
                                     ifelse(data_knivsasen_2022_selection_gradients$p < 0.01 & data_knivsasen_2022_selection_gradients$p > 0.001, "**",
                                            ifelse(data_knivsasen_2022_selection_gradients$p < 0.001, "***", "")))))
```

```{r}
data_knivsasen_2022_selection_gradients <- left_join(data_knivsasen_2022_selection_gradients,
                                                     data_knivsasen_2022_summary_traits,
                                                     by = c("Trait" = "Trait"))
```

```{r}
data_knivsasen_2022_selection_gradients <- data_knivsasen_2022_selection_gradients %>% 
  mutate(Mean_Selection_Gradient = round(Estimate * Trait_Mean, digits = 4)) %>% 
  mutate(Mean_SE_Selection_Gradient = round(SE_Model * Trait_Mean, digits = 4)) %>% 
  mutate(Treatment = "Open_Control") %>% 
  mutate(Population = "Knivsasen_2022")
```

```{r}
saveRDS(data_knivsasen_2022_selection_gradients, 
        file = paste0(here::here("Data/RDS_Objects/Selection_Gradients_Knivsasen_2022.rds")))
```