---
title: "Phenotypic Selection on Floral Traits: Analysis at the Plant Level"
---

```{r include=FALSE}
library(readxl)
library(dplyr)
library(nlme)
library(reshape2)
```

# Load Data: Knivsåsen 2021 

```{r}
data_knivsasen_2021 <- readxl::read_excel(paste0(here::here("Data/Raw_Data/Selection_2022_15-02-23.xlsx")), sheet = "Knivsasen_2021")
```

```{r}
data_knivsasen_2021 <- suppressWarnings(data_knivsasen_2021 %>% 
                                          mutate_at(c("Capsules_Collected",
                                                      "Seeds_Weight",
                                                      "Stem_Height",
                                                      "Flowers_First_Visit",
                                                      "Buds_First_Visit",
                                                      "Capsules_First_Visit",
                                                      "Corolla_Diameter",
                                                      "Tube_Width",
                                                      "Tube_Length",
                                                      "NSD",
                                                      "Stickidium",
                                                      "Open_Capsules_Second_Visit",
                                                      "Closed_Capsules_Second_Visit",
                                                      "Eaten_Capsules_Second_Visit",
                                                      "Unsuccessful_Capsules_Second_Visit",
                                                      "Buds_Second_Visit"),
                                                    as.numeric))
```

# Plant Reproductive Success: Knivsåsen 2021

```{r}
data_knivsasen_2021 <- data_knivsasen_2021 %>% 
  mutate(Total_Flowers = 
           Open_Capsules_Second_Visit + 
           Closed_Capsules_Second_Visit + 
           Eaten_Capsules_Second_Visit + 
           Unsuccessful_Capsules_Second_Visit +
           Buds_Second_Visit) %>% 
  mutate(Total_Fruits = 
           Open_Capsules_Second_Visit + 
           Closed_Capsules_Second_Visit + 
           Eaten_Capsules_Second_Visit) %>% 
  mutate(Mean_Seeds_Weight = round(Seeds_Weight / Capsules_Collected, digits = 4)) %>% 
  mutate(Fruit_Yield_Total_Fruits = Total_Fruits * Mean_Seeds_Weight)
```

```{r}
data_knivsasen_2021 <- data_knivsasen_2021 %>% 
  group_by(Plant_ID) %>% 
  summarise(Consecutive = first(Consecutive),
            Population = first(Population),
            Number_Stems = n_distinct(Stem_ID),
            Seeds_Weight = mean(Seeds_Weight, na.rm = TRUE),
            Stem_Height = mean(Stem_Height, na.rm = TRUE),
            Corolla_Diameter = mean(Corolla_Diameter, na.rm = TRUE),
            Tube_Width = mean(Tube_Width, na.rm = TRUE),
            Tube_Length = mean(Tube_Length, na.rm = TRUE),
            NSD = mean(NSD, na.rm = TRUE),
            Stickidium = mean(Stickidium, na.rm = TRUE),
            Total_Flowers = mean(Total_Flowers, na.rm = TRUE),
            Total_Fruits = mean(Total_Fruits, na.rm = TRUE),
            Mean_Seeds_Weight = mean(Mean_Seeds_Weight, na.rm = TRUE),
            Fruit_Yield_Total_Fruits = mean(Fruit_Yield_Total_Fruits, na.rm = TRUE)) %>% 
  arrange(Consecutive) %>% 
  mutate_if(is.numeric, round, digits = 4)
```

```{r}
data_knivsasen_2021 <- data_knivsasen_2021 %>% 
  ungroup()
```

```{r}
data_knivsasen_2021 <- data_knivsasen_2021 %>% 
  mutate(Relative_Total_Flowers = round(Total_Flowers / mean(Total_Flowers, na.rm = TRUE), digits = 4)) %>% 
  mutate(Relative_Total_Fruits = round(Total_Fruits / mean(Total_Fruits, na.rm = TRUE), digits = 4)) %>% 
  mutate(Relative_Mean_Seeds_Weight = round(Mean_Seeds_Weight / mean(Mean_Seeds_Weight, na.rm = TRUE), digits = 4)) %>% 
  mutate(Relative_Fruit_Yield_Total_Fruits = round(Fruit_Yield_Total_Fruits / mean(Fruit_Yield_Total_Fruits, na.rm = TRUE), digits = 4))
```

# Mean Centre Predictor Variables: Knivsåsen 2021

```{r}
data_knivsasen_2021 <- data_knivsasen_2021 %>% 
  mutate(Stem_Height_Mean_Centred = scale(Stem_Height, scale = FALSE)) %>% 
  mutate(Corolla_Diameter_Mean_Centred = scale(Corolla_Diameter, scale = FALSE)) %>% 
  mutate(Tube_Width_Mean_Centred = scale(Tube_Width, scale = FALSE)) %>% 
  mutate(Tube_Length_Mean_Centred = scale(Tube_Length, scale = FALSE)) %>% 
  mutate(NSD_Mean_Centred = scale(NSD, scale = FALSE)) %>% 
  mutate(Stickidium_Mean_Centred = scale(Stickidium, scale = FALSE)) %>% 
  mutate(Total_Flowers_Mean_Centred = scale(Total_Flowers, scale = FALSE))
```

# Mean-Standardized Phenotypic Selection Gradients: Knivsåsen 2021

```{r}
data_knivsasen_2021_selection_models_linear <- lm(Relative_Fruit_Yield_Total_Fruits ~
                                                    Stem_Height_Mean_Centred +
                                                    Corolla_Diameter_Mean_Centred + 
                                                    Tube_Width_Mean_Centred +
                                                    Tube_Length_Mean_Centred +
                                                    NSD_Mean_Centred +
                                                    Stickidium_Mean_Centred +
                                                    Total_Flowers_Mean_Centred,
                                                  na.action = na.omit,
                                                  data = data_knivsasen_2021)
```

# Mean and Standard Deviation of Floral Traits: Knivsåsen 2021

```{r}
data_knivsasen_2021_mean_traits <- data_knivsasen_2021 %>% 
  summarise_at(c("Stem_Height",
                 "Corolla_Diameter",
                 "Tube_Width",
                 "Tube_Length",
                 "NSD",
                 "Stickidium",
                 "Total_Flowers"),
               mean, na.rm = TRUE)
```

```{r message=FALSE}
data_knivsasen_2021_mean_traits <- melt(data_knivsasen_2021_mean_traits, value.name = "Trait_Mean", variable.name = "Trait")
```

```{r}
data_knivsasen_2021_sd_traits <- data_knivsasen_2021 %>% 
  summarise_at(c("Stem_Height",
                 "Corolla_Diameter",
                 "Tube_Width",
                 "Tube_Length",
                 "NSD",
                 "Stickidium",
                 "Total_Flowers"),
               sd, na.rm = TRUE)
```

```{r message=FALSE}
data_knivsasen_2021_sd_traits <- melt(data_knivsasen_2021_sd_traits, value.name = "Trait_SD", variable.name = "Trait")
```

```{r}
data_knivsasen_2021_summary_traits <- left_join(data_knivsasen_2021_mean_traits,
                                                data_knivsasen_2021_sd_traits,
                                                by = c("Trait" = "Trait"))
```

```{r}
data_knivsasen_2021_summary_traits <- data_knivsasen_2021_summary_traits %>% 
  mutate_if(is.numeric, round, digits = 4)
```

# Mean-Standardized Phenotypic Selection Gradients: Knivsåsen 2021

```{r}
data_knivsasen_2021_selection_gradients <-
  data.frame(Trait = c("Stem_Height",
                       "Corolla_Diameter",
                       "Tube_Width",
                       "Tube_Length",
                       "NSD",
                       "Stickidium",
                       "Total_Flowers"),
             Estimate = c(data_knivsasen_2021_selection_models_linear$coefficients[[2]],
                          data_knivsasen_2021_selection_models_linear$coefficients[[3]],
                          data_knivsasen_2021_selection_models_linear$coefficients[[4]],
                          data_knivsasen_2021_selection_models_linear$coefficients[[5]],
                          data_knivsasen_2021_selection_models_linear$coefficients[[6]],
                          data_knivsasen_2021_selection_models_linear$coefficients[[7]],
                          data_knivsasen_2021_selection_models_linear$coefficients[[8]]),
             SE_Model = c(sqrt(diag(vcov(data_knivsasen_2021_selection_models_linear))[[2]]),
                          sqrt(diag(vcov(data_knivsasen_2021_selection_models_linear))[[3]]),
                          sqrt(diag(vcov(data_knivsasen_2021_selection_models_linear))[[4]]),
                          sqrt(diag(vcov(data_knivsasen_2021_selection_models_linear))[[5]]),
                          sqrt(diag(vcov(data_knivsasen_2021_selection_models_linear))[[6]]),
                          sqrt(diag(vcov(data_knivsasen_2021_selection_models_linear))[[7]]),
                          sqrt(diag(vcov(data_knivsasen_2021_selection_models_linear))[[8]])),
             p = c(summary(data_knivsasen_2021_selection_models_linear)$coefficients[2, "Pr(>|t|)"],
                   summary(data_knivsasen_2021_selection_models_linear)$coefficients[3, "Pr(>|t|)"],
                   summary(data_knivsasen_2021_selection_models_linear)$coefficients[4, "Pr(>|t|)"],
                   summary(data_knivsasen_2021_selection_models_linear)$coefficients[5, "Pr(>|t|)"],
                   summary(data_knivsasen_2021_selection_models_linear)$coefficients[6, "Pr(>|t|)"],
                   summary(data_knivsasen_2021_selection_models_linear)$coefficients[7, "Pr(>|t|)"],
                   summary(data_knivsasen_2021_selection_models_linear)$coefficients[8, "Pr(>|t|)"]))
```

```{r}
data_knivsasen_2021_selection_gradients <- data_knivsasen_2021_selection_gradients %>% 
  mutate_if(is.numeric, round, digits = 4)
```

```{r}
data_knivsasen_2021_selection_gradients <- left_join(data_knivsasen_2021_selection_gradients,
                                                     data_knivsasen_2021_summary_traits,
                                                     by = c("Trait" = "Trait"))
```

```{r}
data_knivsasen_2021_selection_gradients <- data_knivsasen_2021_selection_gradients %>% 
  mutate(Mean_Selection_Gradient = round(Estimate * Trait_Mean, digits = 4)) %>% 
  mutate(Mean_SE_Selection_Gradient = round(SE_Model * Trait_Mean, digits = 4)) %>% 
  mutate(Treatment = "Open_Control") %>% 
  mutate(Population = "Knivsasen_2021")
```

# Load Data: Knivsåsen 2022 

```{r}
data_knivsasen_2022 <- readxl::read_excel(paste0(here::here("Data/Raw_Data/Selection_2022_15-02-23.xlsx")), sheet = "Knivsasen_2022")
```

```{r}
data_knivsasen_2022 <- suppressWarnings(data_knivsasen_2022 %>% 
                                          mutate_at(c("Capsules_Collected",
                                                      "Seeds_Weight",
                                                      "Stem_Height",
                                                      "Flowers_First_Visit",
                                                      "Buds_First_Visit",
                                                      "Eaten_Buds_First_Visit",
                                                      "Capsules_First_Visit",
                                                      "Corolla_Diameter",
                                                      "Tube_Width",
                                                      "Tube_Length",
                                                      "NSD",
                                                      "Stickidium",
                                                      "Open_Capsules_Second_Visit",
                                                      "Closed_Capsules_Second_Visit",
                                                      "Eaten_Capsules_Second_Visit",
                                                      "Failed_Flowers_Second_Visit",
                                                      "Flowers_Second_Visit",
                                                      "Buds_Second_Visit"),
                                                    as.numeric))
```

# Plant Reproductive Success: Knivsåsen 2022

```{r}
data_knivsasen_2022 <- data_knivsasen_2022 %>% 
  mutate(Total_Flowers = 
           Open_Capsules_Second_Visit + 
           Closed_Capsules_Second_Visit + 
           Eaten_Capsules_Second_Visit + 
           Failed_Flowers_Second_Visit + 
           Flowers_Second_Visit +
           Buds_Second_Visit) %>% 
  mutate(Total_Fruits = 
           Open_Capsules_Second_Visit + 
           Closed_Capsules_Second_Visit + 
           Eaten_Capsules_Second_Visit) %>% 
  mutate(Mean_Seeds_Weight = round(Seeds_Weight / Capsules_Collected, digits = 4)) %>% 
  mutate(Fruit_Yield_Total_Fruits = Total_Fruits * Mean_Seeds_Weight)
```

```{r}
data_knivsasen_2022 <- data_knivsasen_2022 %>% 
  group_by(Plant_ID) %>% 
  summarise(Consecutive = first(Consecutive),
            Population = first(Population),
            Number_Stems = n_distinct(Stem_ID),
            Seeds_Weight = mean(Seeds_Weight, na.rm = TRUE),
            Stem_Height = mean(Stem_Height, na.rm = TRUE),
            Corolla_Diameter = mean(Corolla_Diameter, na.rm = TRUE),
            Tube_Width = mean(Tube_Width, na.rm = TRUE),
            Tube_Length = mean(Tube_Length, na.rm = TRUE),
            NSD = mean(NSD, na.rm = TRUE),
            Stickidium = mean(Stickidium, na.rm = TRUE),
            Total_Flowers = mean(Total_Flowers, na.rm = TRUE),
            Total_Fruits = mean(Total_Fruits, na.rm = TRUE),
            Mean_Seeds_Weight = mean(Mean_Seeds_Weight, na.rm = TRUE),
            Fruit_Yield_Total_Fruits = mean(Fruit_Yield_Total_Fruits, na.rm = TRUE)) %>% 
  arrange(Consecutive) %>% 
  mutate_if(is.numeric, round, digits = 4)
```

```{r}
data_knivsasen_2022 <- data_knivsasen_2022 %>% 
  ungroup()
```

```{r}
data_knivsasen_2022 <- data_knivsasen_2022 %>% 
  mutate(Relative_Total_Flowers = round(Total_Flowers / mean(Total_Flowers, na.rm = TRUE), digits = 4)) %>% 
  mutate(Relative_Total_Fruits = round(Total_Fruits / mean(Total_Fruits, na.rm = TRUE), digits = 4)) %>% 
  mutate(Relative_Mean_Seeds_Weight = round(Mean_Seeds_Weight / mean(Mean_Seeds_Weight, na.rm = TRUE), digits = 4)) %>% 
  mutate(Relative_Fruit_Yield_Total_Fruits = round(Fruit_Yield_Total_Fruits / mean(Fruit_Yield_Total_Fruits, na.rm = TRUE), digits = 4))
```

# Mean Centre Predictor Variables: Knivsåsen 2022

```{r}
data_knivsasen_2022 <- data_knivsasen_2022 %>% 
  mutate(Stem_Height_Mean_Centred = scale(Stem_Height, scale = FALSE)) %>% 
  mutate(Corolla_Diameter_Mean_Centred = scale(Corolla_Diameter, scale = FALSE)) %>% 
  mutate(Tube_Width_Mean_Centred = scale(Tube_Width, scale = FALSE)) %>% 
  mutate(Tube_Length_Mean_Centred = scale(Tube_Length, scale = FALSE)) %>% 
  mutate(NSD_Mean_Centred = scale(NSD, scale = FALSE)) %>% 
  mutate(Stickidium_Mean_Centred = scale(Stickidium, scale = FALSE)) %>% 
  mutate(Total_Flowers_Mean_Centred = scale(Total_Flowers, scale = FALSE))
```

# Mean-Standardized Phenotypic Selection Gradients: Knivsåsen 2022

```{r}
data_knivsasen_2022_selection_models_linear <- lm(Relative_Fruit_Yield_Total_Fruits ~
                                                    Stem_Height_Mean_Centred +
                                                    Corolla_Diameter_Mean_Centred + 
                                                    Tube_Width_Mean_Centred +
                                                    Tube_Length_Mean_Centred +
                                                    NSD_Mean_Centred +
                                                    Stickidium_Mean_Centred +
                                                    Total_Flowers_Mean_Centred,
                                                  na.action = na.omit,
                                                  data = data_knivsasen_2022)
```

# Mean and Standard Deviation of Floral Traits: Knivsåsen 2022

```{r}
data_knivsasen_2022_mean_traits <- data_knivsasen_2022 %>% 
  summarise_at(c("Stem_Height",
                 "Corolla_Diameter",
                 "Tube_Width",
                 "Tube_Length",
                 "NSD",
                 "Stickidium",
                 "Total_Flowers"),
               mean, na.rm = TRUE)
```

```{r message=FALSE}
data_knivsasen_2022_mean_traits <- melt(data_knivsasen_2022_mean_traits, value.name = "Trait_Mean", variable.name = "Trait")
```

```{r}
data_knivsasen_2022_sd_traits <- data_knivsasen_2022 %>% 
  summarise_at(c("Stem_Height",
                 "Corolla_Diameter",
                 "Tube_Width",
                 "Tube_Length",
                 "NSD",
                 "Stickidium",
                 "Total_Flowers"),
               sd, na.rm = TRUE)
```

```{r message=FALSE}
data_knivsasen_2022_sd_traits <- melt(data_knivsasen_2022_sd_traits, value.name = "Trait_SD", variable.name = "Trait")
```

```{r}
data_knivsasen_2022_summary_traits <- left_join(data_knivsasen_2022_mean_traits,
                                                data_knivsasen_2022_sd_traits,
                                                by = c("Trait" = "Trait"))
```

```{r}
data_knivsasen_2022_summary_traits <- data_knivsasen_2022_summary_traits %>% 
  mutate_if(is.numeric, round, digits = 4)
```

# Mean-Standardized Phenotypic Selection Gradients: Knivsåsen 2022

```{r}
data_knivsasen_2022_selection_gradients <-
  data.frame(Trait = c("Stem_Height",
                       "Corolla_Diameter",
                       "Tube_Width",
                       "Tube_Length",
                       "NSD",
                       "Stickidium",
                       "Total_Flowers"),
             Estimate = c(data_knivsasen_2022_selection_models_linear$coefficients[[2]],
                          data_knivsasen_2022_selection_models_linear$coefficients[[3]],
                          data_knivsasen_2022_selection_models_linear$coefficients[[4]],
                          data_knivsasen_2022_selection_models_linear$coefficients[[5]],
                          data_knivsasen_2022_selection_models_linear$coefficients[[6]],
                          data_knivsasen_2022_selection_models_linear$coefficients[[7]],
                          data_knivsasen_2022_selection_models_linear$coefficients[[8]]),
             SE_Model = c(sqrt(diag(vcov(data_knivsasen_2022_selection_models_linear))[[2]]),
                          sqrt(diag(vcov(data_knivsasen_2022_selection_models_linear))[[3]]),
                          sqrt(diag(vcov(data_knivsasen_2022_selection_models_linear))[[4]]),
                          sqrt(diag(vcov(data_knivsasen_2022_selection_models_linear))[[5]]),
                          sqrt(diag(vcov(data_knivsasen_2022_selection_models_linear))[[6]]),
                          sqrt(diag(vcov(data_knivsasen_2022_selection_models_linear))[[7]]),
                          sqrt(diag(vcov(data_knivsasen_2022_selection_models_linear))[[8]])),
             p = c(summary(data_knivsasen_2022_selection_models_linear)$coefficients[2, "Pr(>|t|)"],
                   summary(data_knivsasen_2022_selection_models_linear)$coefficients[3, "Pr(>|t|)"],
                   summary(data_knivsasen_2022_selection_models_linear)$coefficients[4, "Pr(>|t|)"],
                   summary(data_knivsasen_2022_selection_models_linear)$coefficients[5, "Pr(>|t|)"],
                   summary(data_knivsasen_2022_selection_models_linear)$coefficients[6, "Pr(>|t|)"],
                   summary(data_knivsasen_2022_selection_models_linear)$coefficients[7, "Pr(>|t|)"],
                   summary(data_knivsasen_2022_selection_models_linear)$coefficients[8, "Pr(>|t|)"]))
```

```{r}
data_knivsasen_2022_selection_gradients <- data_knivsasen_2022_selection_gradients %>% 
  mutate_if(is.numeric, round, digits = 4)
```

```{r}
data_knivsasen_2022_selection_gradients <- left_join(data_knivsasen_2022_selection_gradients,
                                                     data_knivsasen_2022_summary_traits,
                                                     by = c("Trait" = "Trait"))
```

```{r}
data_knivsasen_2022_selection_gradients <- data_knivsasen_2022_selection_gradients %>% 
  mutate(Mean_Selection_Gradient = round(Estimate * Trait_Mean, digits = 4)) %>% 
  mutate(Mean_SE_Selection_Gradient = round(SE_Model * Trait_Mean, digits = 4)) %>% 
  mutate(Treatment = "Open_Control") %>% 
  mutate(Population = "Knivsasen_2022")
```

# Load Data: Veberöd 2022 

```{r}
data_veberod_2022 <- readxl::read_excel(paste0(here::here("Data/Raw_Data/Selection_2022_15-02-23.xlsx")), sheet = "Veberod_2022")
```

```{r}
data_veberod_2022 <- suppressWarnings(data_veberod_2022 %>% 
                                        mutate_at(c("Capsules_Collected",
                                                    "Seeds_Weight",
                                                    "Stem_Height",
                                                    "Flowers_First_Visit",
                                                    "Buds_First_Visit",
                                                    "Eaten_Buds_First_Visit",
                                                    "Capsules_First_Visit",
                                                    "Corolla_Diameter",
                                                    "Tube_Width",
                                                    "Tube_Length",
                                                    "NSD",
                                                    "Stickidium",
                                                    "Open_Capsules_Second_Visit",
                                                    "Closed_Capsules_Second_Visit",
                                                    "Eaten_Capsules_Second_Visit",
                                                    "Failed_Flowers_Second_Visit",
                                                    "Flowers_Second_Visit",
                                                    "Buds_Second_Visit"),
                                                  as.numeric))
```

# Plant Reproductive Success: Veberöd 2022

```{r}
data_veberod_2022 <- data_veberod_2022 %>% 
  mutate(Total_Flowers = 
           Open_Capsules_Second_Visit +
           Closed_Capsules_Second_Visit +
           Eaten_Capsules_Second_Visit +
           Failed_Flowers_Second_Visit +
           Flowers_Second_Visit +
           Buds_Second_Visit) %>% 
  mutate(Total_Fruits = 
           Open_Capsules_Second_Visit + 
           Closed_Capsules_Second_Visit + 
           Eaten_Capsules_Second_Visit) %>% 
  mutate(Mean_Seeds_Weight = round(Seeds_Weight / Capsules_Collected, digits = 4)) %>% 
  mutate(Fruit_Yield_Total_Fruits = Total_Fruits * Mean_Seeds_Weight)
```

```{r}
data_veberod_2022 <- data_veberod_2022 %>% 
  group_by(Plant_ID) %>% 
  summarise(Consecutive = first(Consecutive),
            Population = first(Population),
            Treatment = first(Treatment),
            Block = first(Block),
            Number_Stems = n_distinct(Stem_ID),
            Seeds_Weight = mean(Seeds_Weight, na.rm = TRUE),
            Stem_Height = mean(Stem_Height, na.rm = TRUE),
            Corolla_Diameter = mean(Corolla_Diameter, na.rm = TRUE),
            Tube_Width = mean(Tube_Width, na.rm = TRUE),
            Tube_Length = mean(Tube_Length, na.rm = TRUE),
            NSD = mean(NSD, na.rm = TRUE),
            Stickidium = mean(Stickidium, na.rm = TRUE),
            Total_Flowers = mean(Total_Flowers, na.rm = TRUE),
            Total_Fruits = mean(Total_Fruits, na.rm = TRUE),
            Mean_Seeds_Weight = mean(Mean_Seeds_Weight, na.rm = TRUE),
            Fruit_Yield_Total_Fruits = mean(Fruit_Yield_Total_Fruits, na.rm = TRUE)) %>% 
  arrange(Consecutive) %>% 
  mutate_if(is.numeric, round, digits = 4)
```

```{r}
data_veberod_2022 <- data_veberod_2022 %>% 
  ungroup()
```

```{r}
data_veberod_2022 <- data_veberod_2022 %>% 
  group_by(Treatment) %>% 
  mutate(Relative_Total_Flowers = round(Total_Flowers / mean(Total_Flowers, na.rm = TRUE), digits = 4)) %>% 
  mutate(Relative_Total_Fruits = round(Total_Fruits / mean(Total_Fruits, na.rm = TRUE), digits = 4)) %>% 
  mutate(Relative_Mean_Seeds_Weight = round(Mean_Seeds_Weight / mean(Mean_Seeds_Weight, na.rm = TRUE), digits = 4)) %>% 
  mutate(Relative_Fruit_Yield_Total_Fruits = round(Fruit_Yield_Total_Fruits / mean(Fruit_Yield_Total_Fruits, na.rm = TRUE), digits = 4))
```

```{r}
data_veberod_2022 <- data_veberod_2022 %>% 
  ungroup()
```

# Mean Centre Predictor Variables: Veberöd 2022

```{r}
data_veberod_2022 <- data_veberod_2022 %>% 
  group_by(Treatment) %>% 
  mutate(Stem_Height_Mean_Centred = scale(Stem_Height, scale = FALSE)) %>% 
  mutate(Corolla_Diameter_Mean_Centred = scale(Corolla_Diameter, scale = FALSE)) %>% 
  mutate(Tube_Width_Mean_Centred = scale(Tube_Width, scale = FALSE)) %>% 
  mutate(Tube_Length_Mean_Centred = scale(Tube_Length, scale = FALSE)) %>% 
  mutate(NSD_Mean_Centred = scale(NSD, scale = FALSE)) %>% 
  mutate(Stickidium_Mean_Centred = scale(Stickidium, scale = FALSE)) %>% 
  mutate(Total_Flowers_Mean_Centred = scale(Total_Flowers, scale = FALSE))
```

```{r}
data_veberod_2022 <- data_veberod_2022 %>% 
  ungroup()
```

# Mean-Standardized Phenotypic Selection Gradients: Veberöd 2022

```{r}
data_veberod_2022_selection_models <- data_veberod_2022 %>% 
  split(data_veberod_2022$Treatment)
```

```{r}
data_veberod_2022_selection_models_linear <- lapply(data_veberod_2022_selection_models,
                                                    function(df)
                                                      lm(Relative_Fruit_Yield_Total_Fruits ~
                                                           Stem_Height_Mean_Centred +
                                                           Corolla_Diameter_Mean_Centred + 
                                                           Tube_Width_Mean_Centred +
                                                           Tube_Length_Mean_Centred +
                                                           NSD_Mean_Centred +
                                                           Stickidium_Mean_Centred +
                                                           Total_Flowers_Mean_Centred,
                                                                na.action = na.omit,
                                                                data = df))
```

# Mean and Standard Deviation of Floral Traits: Veberöd 2022

```{r}
data_veberod_2022_mean_traits <- data_veberod_2022 %>% 
  group_by(Treatment) %>% 
  summarise_at(c("Stem_Height",
                 "Corolla_Diameter",
                 "Tube_Width",
                 "Tube_Length",
                 "NSD",
                 "Stickidium",
                 "Total_Flowers"),
               mean, na.rm = TRUE)
```

```{r}
data_veberod_2022_mean_traits <-data_veberod_2022_mean_traits %>% 
  reshape2::melt(id.vars = "Treatment",
                 measure.vars = c("Stem_Height", "Corolla_Diameter", "Tube_Width", "Tube_Length", "NSD", "Stickidium", "Total_Flowers"),
                 variable.name = "Trait",
                 value.name = "Trait_Mean")
```

```{r}
data_veberod_2022_sd_traits <- data_veberod_2022 %>% 
  group_by(Treatment) %>% 
  summarise_at(c("Stem_Height",
                 "Corolla_Diameter",
                 "Tube_Width",
                 "Tube_Length",
                 "NSD",
                 "Stickidium",
                 "Total_Flowers"),
               sd, na.rm = TRUE)
```

```{r}
data_veberod_2022_sd_traits <-data_veberod_2022_sd_traits %>% 
  reshape2::melt(id.vars = "Treatment",
                 measure.vars = c("Stem_Height", "Corolla_Diameter", "Tube_Width", "Tube_Length", "NSD", "Stickidium", "Total_Flowers"),
                 variable.name = "Trait",
                 value.name = "Trait_SD")
```

```{r}
data_veberod_2022_summary_traits <- left_join(data_veberod_2022_mean_traits,
                                              data_veberod_2022_sd_traits,
                                              by = c("Trait" = "Trait",
                                                     "Treatment" = "Treatment"))
```

```{r}
data_veberod_2022_summary_traits <- data_veberod_2022_summary_traits %>% 
  mutate_if(is.numeric, round, digits = 4)
```

# Mean-Standardized Phenotypic Selection Gradients: Veberöd 2022

```{r}
data_veberod_2022_selection_gradients <-
  data.frame(Trait = rep(c("Stem_Height",
                           "Corolla_Diameter",
                           "Tube_Width",
                           "Tube_Length",
                           "NSD",
                           "Stickidium",
                           "Total_Flowers"),
                         times = 4),
             Treatment = rep(c("Open_Control",
                               "Day_Caged",
                               "Night_Caged",
                               "Always_Caged"),
                             times = c(7, 7, 7, 7)),
             Estimate = c(data_veberod_2022_selection_models_linear$Open_Control$coefficients[2],
                          data_veberod_2022_selection_models_linear$Open_Control$coefficients[3],
                          data_veberod_2022_selection_models_linear$Open_Control$coefficients[4],
                          data_veberod_2022_selection_models_linear$Open_Control$coefficients[5],
                          data_veberod_2022_selection_models_linear$Open_Control$coefficients[6],
                          data_veberod_2022_selection_models_linear$Open_Control$coefficients[7],
                          data_veberod_2022_selection_models_linear$Open_Control$coefficients[8],
                          data_veberod_2022_selection_models_linear$Day_Caged$coefficients[2],
                          data_veberod_2022_selection_models_linear$Day_Caged$coefficients[3],
                          data_veberod_2022_selection_models_linear$Day_Caged$coefficients[4],
                          data_veberod_2022_selection_models_linear$Day_Caged$coefficients[5],
                          data_veberod_2022_selection_models_linear$Day_Caged$coefficients[6],
                          data_veberod_2022_selection_models_linear$Day_Caged$coefficients[7],
                          data_veberod_2022_selection_models_linear$Day_Caged$coefficients[8],
                          data_veberod_2022_selection_models_linear$Night_Caged$coefficients[2],
                          data_veberod_2022_selection_models_linear$Night_Caged$coefficients[3],
                          data_veberod_2022_selection_models_linear$Night_Caged$coefficients[4],
                          data_veberod_2022_selection_models_linear$Night_Caged$coefficients[5],
                          data_veberod_2022_selection_models_linear$Night_Caged$coefficients[6],
                          data_veberod_2022_selection_models_linear$Night_Caged$coefficients[7],
                          data_veberod_2022_selection_models_linear$Night_Caged$coefficients[8],
                          data_veberod_2022_selection_models_linear$Always_Caged$coefficients[2],
                          data_veberod_2022_selection_models_linear$Always_Caged$coefficients[3],
                          data_veberod_2022_selection_models_linear$Always_Caged$coefficients[4],
                          data_veberod_2022_selection_models_linear$Always_Caged$coefficients[5],
                          data_veberod_2022_selection_models_linear$Always_Caged$coefficients[6],
                          data_veberod_2022_selection_models_linear$Always_Caged$coefficients[7],
                          data_veberod_2022_selection_models_linear$Always_Caged$coefficients[8]),
             SE_Model = c(sqrt(diag(vcov(data_veberod_2022_selection_models_linear$Open_Control))[2]),
                          sqrt(diag(vcov(data_veberod_2022_selection_models_linear$Open_Control))[3]),
                          sqrt(diag(vcov(data_veberod_2022_selection_models_linear$Open_Control))[4]),
                          sqrt(diag(vcov(data_veberod_2022_selection_models_linear$Open_Control))[5]),
                          sqrt(diag(vcov(data_veberod_2022_selection_models_linear$Open_Control))[6]),
                          sqrt(diag(vcov(data_veberod_2022_selection_models_linear$Open_Control))[7]),
                          sqrt(diag(vcov(data_veberod_2022_selection_models_linear$Open_Control))[8]),
                          sqrt(diag(vcov(data_veberod_2022_selection_models_linear$Day_Caged))[2]),
                          sqrt(diag(vcov(data_veberod_2022_selection_models_linear$Day_Caged))[3]),
                          sqrt(diag(vcov(data_veberod_2022_selection_models_linear$Day_Caged))[4]),
                          sqrt(diag(vcov(data_veberod_2022_selection_models_linear$Day_Caged))[5]),
                          sqrt(diag(vcov(data_veberod_2022_selection_models_linear$Day_Caged))[6]),
                          sqrt(diag(vcov(data_veberod_2022_selection_models_linear$Day_Caged))[7]),
                          sqrt(diag(vcov(data_veberod_2022_selection_models_linear$Day_Caged))[8]),
                          sqrt(diag(vcov(data_veberod_2022_selection_models_linear$Night_Caged))[2]),
                          sqrt(diag(vcov(data_veberod_2022_selection_models_linear$Night_Caged))[3]),
                          sqrt(diag(vcov(data_veberod_2022_selection_models_linear$Night_Caged))[4]),
                          sqrt(diag(vcov(data_veberod_2022_selection_models_linear$Night_Caged))[5]),
                          sqrt(diag(vcov(data_veberod_2022_selection_models_linear$Night_Caged))[6]),
                          sqrt(diag(vcov(data_veberod_2022_selection_models_linear$Night_Caged))[7]),
                          sqrt(diag(vcov(data_veberod_2022_selection_models_linear$Night_Caged))[8]),
                          sqrt(diag(vcov(data_veberod_2022_selection_models_linear$Always_Caged))[2]),
                          sqrt(diag(vcov(data_veberod_2022_selection_models_linear$Always_Caged))[3]),
                          sqrt(diag(vcov(data_veberod_2022_selection_models_linear$Always_Caged))[4]),
                          sqrt(diag(vcov(data_veberod_2022_selection_models_linear$Always_Caged))[5]),
                          sqrt(diag(vcov(data_veberod_2022_selection_models_linear$Always_Caged))[6]),
                          sqrt(diag(vcov(data_veberod_2022_selection_models_linear$Always_Caged))[7]),
                          sqrt(diag(vcov(data_veberod_2022_selection_models_linear$Always_Caged))[8])),
             p = c(summary(data_veberod_2022_selection_models_linear$Open_Control)$coefficients[2, "Pr(>|t|)"],
                   summary(data_veberod_2022_selection_models_linear$Open_Control)$coefficients[3, "Pr(>|t|)"],
                   summary(data_veberod_2022_selection_models_linear$Open_Control)$coefficients[4, "Pr(>|t|)"],
                   summary(data_veberod_2022_selection_models_linear$Open_Control)$coefficients[5, "Pr(>|t|)"],
                   summary(data_veberod_2022_selection_models_linear$Open_Control)$coefficients[6, "Pr(>|t|)"],
                   summary(data_veberod_2022_selection_models_linear$Open_Control)$coefficients[7, "Pr(>|t|)"],
                   summary(data_veberod_2022_selection_models_linear$Open_Control)$coefficients[8, "Pr(>|t|)"],
                   summary(data_veberod_2022_selection_models_linear$Day_Caged)$coefficients[2, "Pr(>|t|)"],
                   summary(data_veberod_2022_selection_models_linear$Day_Caged)$coefficients[3, "Pr(>|t|)"],
                   summary(data_veberod_2022_selection_models_linear$Day_Caged)$coefficients[4, "Pr(>|t|)"],
                   summary(data_veberod_2022_selection_models_linear$Day_Caged)$coefficients[5, "Pr(>|t|)"],
                   summary(data_veberod_2022_selection_models_linear$Day_Caged)$coefficients[6, "Pr(>|t|)"],
                   summary(data_veberod_2022_selection_models_linear$Day_Caged)$coefficients[7, "Pr(>|t|)"],
                   summary(data_veberod_2022_selection_models_linear$Day_Caged)$coefficients[8, "Pr(>|t|)"],
                   summary(data_veberod_2022_selection_models_linear$Night_Caged)$coefficients[2, "Pr(>|t|)"],
                   summary(data_veberod_2022_selection_models_linear$Night_Caged)$coefficients[3, "Pr(>|t|)"],
                   summary(data_veberod_2022_selection_models_linear$Night_Caged)$coefficients[4, "Pr(>|t|)"],
                   summary(data_veberod_2022_selection_models_linear$Night_Caged)$coefficients[5, "Pr(>|t|)"],
                   summary(data_veberod_2022_selection_models_linear$Night_Caged)$coefficients[6, "Pr(>|t|)"],
                   summary(data_veberod_2022_selection_models_linear$Night_Caged)$coefficients[7, "Pr(>|t|)"],
                   summary(data_veberod_2022_selection_models_linear$Night_Caged)$coefficients[8, "Pr(>|t|)"],
                   summary(data_veberod_2022_selection_models_linear$Always_Caged)$coefficients[2, "Pr(>|t|)"],
                   summary(data_veberod_2022_selection_models_linear$Always_Caged)$coefficients[3, "Pr(>|t|)"],
                   summary(data_veberod_2022_selection_models_linear$Always_Caged)$coefficients[4, "Pr(>|t|)"],
                   summary(data_veberod_2022_selection_models_linear$Always_Caged)$coefficients[5, "Pr(>|t|)"],
                   summary(data_veberod_2022_selection_models_linear$Always_Caged)$coefficients[6, "Pr(>|t|)"],
                   summary(data_veberod_2022_selection_models_linear$Always_Caged)$coefficients[7, "Pr(>|t|)"],
                   summary(data_veberod_2022_selection_models_linear$Always_Caged)$coefficients[8, "Pr(>|t|)"]))
```

```{r}
data_veberod_2022_selection_gradients <- data_veberod_2022_selection_gradients %>% 
  mutate_if(is.numeric, round, digits = 4)
```

```{r}
data_veberod_2022_selection_gradients <- left_join(data_veberod_2022_selection_gradients,
                                                   data_veberod_2022_summary_traits,
                                              by = c("Treatment" = "Treatment",
                                                     "Trait" = "Trait"))
```

```{r}
data_veberod_2022_selection_gradients <- data_veberod_2022_selection_gradients %>% 
  mutate(Mean_Selection_Gradient = round(Estimate * Trait_Mean, digits = 4)) %>% 
  mutate(Mean_SE_Selection_Gradient = round(SE_Model * Trait_Mean, digits = 4)) %>% 
  mutate(Population = "Veberod_2022")
```

# Compile Mean-Standardized Phenotypic Selecion Gradients

```{r}
data_selection_gradients <- rbind(data_knivsasen_2021_selection_gradients,
                                  data_knivsasen_2022_selection_gradients,
                                  data_veberod_2022_selection_gradients)
```

```{r}
data_selection_gradients <- data_selection_gradients %>% 
  mutate(Significant = ifelse(p >= 0.05 & p <= 0.10, paste0(expression("\u2020")),
                              ifelse(p < 0.05 & p > 0.01, "*",
                                     ifelse(p < 0.01 & p > 0.001, "**",
                                            ifelse(p < 0.001, "***", "")))))
```

```{r}
saveRDS(data_selection_gradients, file = paste0(here::here("Data/RDS_Objects/Selection_Gradients_Plant_Level.rds")))
```