---
title: "Phenotypic Selection on Floral Traits: Veberöd 2022"
---

```{r include=FALSE}
library(readxl)
library(dplyr)
library(ggplot2)
library(nlme)
library(reshape2)
library(MuMIn)
library(performance)
```

# Load Data: Veberöd 2022

```{r}
data_veberod_2022 <- readxl::read_excel(paste0(here::here("GitHub/Data/Selection_2022_15-02-23.xlsx")), sheet = "Veberod_2022")
```

```{r}
data_veberod_2022 <- suppressWarnings(data_veberod_2022 %>% 
                                        mutate_at(c("Capsules_Collected",
                                                    "Seeds_Weight",
                                                    "Stem_Height",
                                                    "Flowers_First_Visit",
                                                    "Buds_First_Visit",
                                                    "Eaten_Buds_First_Visit",
                                                    "Capsules_First_Visit",
                                                    "Corolla_Diameter",
                                                    "Tube_Width",
                                                    "Tube_Length",
                                                    "NSD",
                                                    "Stickidium",
                                                    "Open_Capsules_Second_Visit",
                                                    "Closed_Capsules_Second_Visit",
                                                    "Eaten_Capsules_Second_Visit",
                                                    "Failed_Flowers_Second_Visit",
                                                    "Flowers_Second_Visit",
                                                    "Buds_Second_Visit"),
                                                  as.numeric))
```

# Plant Reproductive Success: Veberöd 2022

```{r}
data_veberod_2022 <- data_veberod_2022 %>%  
  mutate(Total_Flowers = 
           Open_Capsules_Second_Visit +
           Closed_Capsules_Second_Visit +
           Eaten_Capsules_Second_Visit +
           Failed_Flowers_Second_Visit +
           Flowers_Second_Visit +
           Buds_Second_Visit) %>% 
  mutate(Total_Fruits = 
           Open_Capsules_Second_Visit + 
           Closed_Capsules_Second_Visit + 
           Eaten_Capsules_Second_Visit) %>% 
  mutate(Mean_Seeds_Weight = round(Seeds_Weight / Capsules_Collected, digits = 4)) %>% 
  mutate(Fruit_Yield_Total_Fruits = Total_Fruits * Mean_Seeds_Weight) 
```

```{r}
data_veberod_2022 <- data_veberod_2022 %>% 
  group_by(Treatment) %>% 
  mutate(Relative_Total_Flowers = round(Total_Flowers / mean(Total_Flowers, na.rm = TRUE), digits = 4)) %>% 
  mutate(Relative_Total_Fruits = round(Total_Fruits / mean(Total_Fruits, na.rm = TRUE), digits = 4)) %>% 
  mutate(Relative_Mean_Seeds_Weight = round(Mean_Seeds_Weight / mean(Mean_Seeds_Weight, na.rm = TRUE), digits = 4)) %>% 
  mutate(Relative_Fruit_Yield_Total_Fruits = round(Fruit_Yield_Total_Fruits / mean(Fruit_Yield_Total_Fruits, na.rm = TRUE), digits = 4))
```

```{r}
data_veberod_2022 <- data_veberod_2022 %>% 
  ungroup()
```

# Mean Centre Predictor Variables

```{r}
data_veberod_2022 <- data_veberod_2022 %>% 
  group_by(Treatment) %>% 
  mutate(Stem_Height_Mean_Centred = scale(Stem_Height, scale = FALSE)) %>% 
  mutate(Corolla_Diameter_Mean_Centred = scale(Corolla_Diameter, scale = FALSE)) %>% 
  mutate(Tube_Width_Mean_Centred = scale(Tube_Width, scale = FALSE)) %>% 
  mutate(Tube_Length_Mean_Centred = scale(Tube_Length, scale = FALSE)) %>% 
  mutate(NSD_Mean_Centred = scale(NSD, scale = FALSE)) %>% 
  mutate(Stickidium_Mean_Centred = scale(Stickidium, scale = FALSE)) %>% 
  mutate(Total_Flowers_Mean_Centred = scale(Total_Flowers, scale = FALSE))
```

```{r}
data_veberod_2022 <- data_veberod_2022 %>% 
  ungroup()
```

```{r}
saveRDS(data_veberod_2022, 
        file = paste0(here::here("GitHub/Data/Data_Phenotypes_Veberod_2022.rds")))
```

# Linear Mixed-Effects Models

```{r}
data_veberod_2022_selection_models <- data_veberod_2022 %>% 
  split(data_veberod_2022$Treatment)
```

## Directional Phenotypic Selection

```{r}
data_veberod_2022_selection_models_linear <- lapply(data_veberod_2022_selection_models,
                                                    function(df)
                                                      nlme::lme(Relative_Fruit_Yield_Total_Fruits ~
                                                                  Stem_Height_Mean_Centred +
                                                                  Corolla_Diameter_Mean_Centred + 
                                                                  Tube_Width_Mean_Centred +
                                                                  Tube_Length_Mean_Centred +
                                                                  NSD_Mean_Centred +
                                                                  Stickidium_Mean_Centred +
                                                                  Total_Flowers_Mean_Centred,
                                                                random = ~ 1 | Plant_ID,
                                                                na.action = na.omit,
                                                                data = df))
```

## Quadratic and Correlational Phenotypic Selection

```{r}
data_veberod_2022_selection_models_quadratic <- lapply(data_veberod_2022_selection_models,
                                                       function(df)
                                                         nlme::lme(Relative_Fruit_Yield_Total_Fruits ~
                                                                     Stem_Height_Mean_Centred +
                                                                     Corolla_Diameter_Mean_Centred + 
                                                                     Tube_Width_Mean_Centred +
                                                                     Tube_Length_Mean_Centred +
                                                                     NSD_Mean_Centred +
                                                                     Stickidium_Mean_Centred +
                                                                     Total_Flowers_Mean_Centred +
                                                                     I(Stem_Height_Mean_Centred^2) +
                                                                     I(Corolla_Diameter_Mean_Centred^2) +
                                                                     I(Tube_Width_Mean_Centred^2) +
                                                                     I(Tube_Length_Mean_Centred^2) +
                                                                     I(NSD_Mean_Centred^2) +
                                                                     I(Stickidium_Mean_Centred^2) +
                                                                     I(Total_Flowers_Mean_Centred^2) +
                                                                     Stem_Height_Mean_Centred:Corolla_Diameter_Mean_Centred +
                                                                     Stem_Height_Mean_Centred:Tube_Width_Mean_Centred +
                                                                     Stem_Height_Mean_Centred:Tube_Length_Mean_Centred +
                                                                     Stem_Height_Mean_Centred:NSD_Mean_Centred +
                                                                     Stem_Height_Mean_Centred:Stickidium_Mean_Centred +
                                                                     Stem_Height_Mean_Centred:Total_Flowers_Mean_Centred +
                                                                     Corolla_Diameter_Mean_Centred:Tube_Width_Mean_Centred +
                                                                     Corolla_Diameter_Mean_Centred:Tube_Length_Mean_Centred +
                                                                     Corolla_Diameter_Mean_Centred:NSD_Mean_Centred +
                                                                     Corolla_Diameter_Mean_Centred:Stickidium_Mean_Centred +
                                                                     Corolla_Diameter_Mean_Centred:Total_Flowers_Mean_Centred +
                                                                     Tube_Width_Mean_Centred:Tube_Length_Mean_Centred +
                                                                     Tube_Width_Mean_Centred:NSD_Mean_Centred +
                                                                     Tube_Width_Mean_Centred:Stickidium_Mean_Centred +
                                                                     Tube_Width_Mean_Centred:Total_Flowers_Mean_Centred +
                                                                     Tube_Length_Mean_Centred:NSD_Mean_Centred +
                                                                     Tube_Length_Mean_Centred:Stickidium_Mean_Centred +
                                                                     Tube_Length_Mean_Centred:Total_Flowers_Mean_Centred +
                                                                     NSD_Mean_Centred:Stickidium_Mean_Centred +
                                                                     NSD_Mean_Centred:Total_Flowers_Mean_Centred +
                                                                     Stickidium_Mean_Centred:Total_Flowers_Mean_Centred,
                                                                   random = ~ 1 | Plant_ID,
                                                                   na.action = na.omit,
                                                                   data = df))
```

## Compare Performance: Directional, Quadratic, and Correlational Phenotypic Selection

```{r}
data_veberod_2022_models_performance <- compare_performance(data_veberod_2022_selection_models_linear$Open_Control,
                                                            data_veberod_2022_selection_models_quadratic$Open_Control,
                                                            metrics = c("AIC", "R2"), estimator = "ML")
```

# Mean and Standard Deviation of Floral Traits: Veberöd 2022

```{r}
data_veberod_2022_mean_traits <- data_veberod_2022 %>% 
  group_by(Treatment) %>% 
  summarise_at(c("Stem_Height",
                 "Corolla_Diameter",
                 "Tube_Width",
                 "Tube_Length",
                 "NSD",
                 "Stickidium",
                 "Total_Flowers"),
               mean, na.rm = TRUE)
```

```{r}
data_veberod_2022_mean_traits <-data_veberod_2022_mean_traits %>% 
  reshape2::melt(id.vars = "Treatment",
                 measure.vars = c("Stem_Height", "Corolla_Diameter", "Tube_Width", "Tube_Length", "NSD", "Stickidium", "Total_Flowers"),
                 variable.name = "Trait",
                 value.name = "Trait_Mean")
```

```{r}
data_veberod_2022_sd_traits <- data_veberod_2022 %>% 
  group_by(Treatment) %>% 
  summarise_at(c("Stem_Height",
                 "Corolla_Diameter",
                 "Tube_Width",
                 "Tube_Length",
                 "NSD",
                 "Stickidium",
                 "Total_Flowers"),
               sd, na.rm = TRUE)
```

```{r}
data_veberod_2022_sd_traits <- data_veberod_2022_sd_traits %>% 
  reshape2::melt(id.vars = "Treatment",
                 measure.vars = c("Stem_Height", "Corolla_Diameter", "Tube_Width", "Tube_Length", "NSD", "Stickidium", "Total_Flowers"),
                 variable.name = "Trait",
                 value.name = "Trait_SD")
```

```{r}
data_veberod_2022_summary_traits <- left_join(data_veberod_2022_mean_traits,
                                              data_veberod_2022_sd_traits,
                                              by = c("Trait" = "Trait",
                                                     "Treatment" = "Treatment"))
```

```{r}
data_veberod_2022_summary_traits <- data_veberod_2022_summary_traits %>% 
  mutate_if(is.numeric, round, digits = 4)
```

# Mean-Standardized Phenotypic Selection Gradients

```{r}
data_veberod_2022_selection_gradients <-
  data.frame(Trait = rep(c("Stem_Height",
                           "Corolla_Diameter",
                           "Tube_Width",
                           "Tube_Length",
                           "NSD",
                           "Stickidium",
                           "Total_Flowers"),
                         times = 4),
             Treatment = rep(c("Open_Control",
                               "Day_Caged",
                               "Night_Caged",
                               "Always_Caged"),
                             times = c(7, 7, 7, 7)),
             Method = rep(c("Linear"), each = 28),
             Estimate = c(data_veberod_2022_selection_models_linear$Open_Control$coefficients$fixed[2],
                          data_veberod_2022_selection_models_linear$Open_Control$coefficients$fixed[3],
                          data_veberod_2022_selection_models_linear$Open_Control$coefficients$fixed[4],
                          data_veberod_2022_selection_models_linear$Open_Control$coefficients$fixed[5],
                          data_veberod_2022_selection_models_linear$Open_Control$coefficients$fixed[6],
                          data_veberod_2022_selection_models_linear$Open_Control$coefficients$fixed[7],
                          data_veberod_2022_selection_models_linear$Open_Control$coefficients$fixed[8],
                          data_veberod_2022_selection_models_linear$Day_Caged$coefficients$fixed[2],
                          data_veberod_2022_selection_models_linear$Day_Caged$coefficients$fixed[3],
                          data_veberod_2022_selection_models_linear$Day_Caged$coefficients$fixed[4],
                          data_veberod_2022_selection_models_linear$Day_Caged$coefficients$fixed[5],
                          data_veberod_2022_selection_models_linear$Day_Caged$coefficients$fixed[6],
                          data_veberod_2022_selection_models_linear$Day_Caged$coefficients$fixed[7],
                          data_veberod_2022_selection_models_linear$Day_Caged$coefficients$fixed[8],
                          data_veberod_2022_selection_models_linear$Night_Caged$coefficients$fixed[2],
                          data_veberod_2022_selection_models_linear$Night_Caged$coefficients$fixed[3],
                          data_veberod_2022_selection_models_linear$Night_Caged$coefficients$fixed[4],
                          data_veberod_2022_selection_models_linear$Night_Caged$coefficients$fixed[5],
                          data_veberod_2022_selection_models_linear$Night_Caged$coefficients$fixed[6],
                          data_veberod_2022_selection_models_linear$Night_Caged$coefficients$fixed[7],
                          data_veberod_2022_selection_models_linear$Night_Caged$coefficients$fixed[8],
                          data_veberod_2022_selection_models_linear$Always_Caged$coefficients$fixed[2],
                          data_veberod_2022_selection_models_linear$Always_Caged$coefficients$fixed[3],
                          data_veberod_2022_selection_models_linear$Always_Caged$coefficients$fixed[4],
                          data_veberod_2022_selection_models_linear$Always_Caged$coefficients$fixed[5],
                          data_veberod_2022_selection_models_linear$Always_Caged$coefficients$fixed[6],
                          data_veberod_2022_selection_models_linear$Always_Caged$coefficients$fixed[7],
                          data_veberod_2022_selection_models_linear$Always_Caged$coefficients$fixed[8]),
             SE_Model = c(sqrt(diag(vcov(data_veberod_2022_selection_models_linear$Open_Control))[2]),
                          sqrt(diag(vcov(data_veberod_2022_selection_models_linear$Open_Control))[3]),
                          sqrt(diag(vcov(data_veberod_2022_selection_models_linear$Open_Control))[4]),
                          sqrt(diag(vcov(data_veberod_2022_selection_models_linear$Open_Control))[5]),
                          sqrt(diag(vcov(data_veberod_2022_selection_models_linear$Open_Control))[6]),
                          sqrt(diag(vcov(data_veberod_2022_selection_models_linear$Open_Control))[7]),
                          sqrt(diag(vcov(data_veberod_2022_selection_models_linear$Open_Control))[8]),
                          sqrt(diag(vcov(data_veberod_2022_selection_models_linear$Day_Caged))[2]),
                          sqrt(diag(vcov(data_veberod_2022_selection_models_linear$Day_Caged))[3]),
                          sqrt(diag(vcov(data_veberod_2022_selection_models_linear$Day_Caged))[4]),
                          sqrt(diag(vcov(data_veberod_2022_selection_models_linear$Day_Caged))[5]),
                          sqrt(diag(vcov(data_veberod_2022_selection_models_linear$Day_Caged))[6]),
                          sqrt(diag(vcov(data_veberod_2022_selection_models_linear$Day_Caged))[7]),
                          sqrt(diag(vcov(data_veberod_2022_selection_models_linear$Day_Caged))[8]),
                          sqrt(diag(vcov(data_veberod_2022_selection_models_linear$Night_Caged))[2]),
                          sqrt(diag(vcov(data_veberod_2022_selection_models_linear$Night_Caged))[3]),
                          sqrt(diag(vcov(data_veberod_2022_selection_models_linear$Night_Caged))[4]),
                          sqrt(diag(vcov(data_veberod_2022_selection_models_linear$Night_Caged))[5]),
                          sqrt(diag(vcov(data_veberod_2022_selection_models_linear$Night_Caged))[6]),
                          sqrt(diag(vcov(data_veberod_2022_selection_models_linear$Night_Caged))[7]),
                          sqrt(diag(vcov(data_veberod_2022_selection_models_linear$Night_Caged))[8]),
                          sqrt(diag(vcov(data_veberod_2022_selection_models_linear$Always_Caged))[2]),
                          sqrt(diag(vcov(data_veberod_2022_selection_models_linear$Always_Caged))[3]),
                          sqrt(diag(vcov(data_veberod_2022_selection_models_linear$Always_Caged))[4]),
                          sqrt(diag(vcov(data_veberod_2022_selection_models_linear$Always_Caged))[5]),
                          sqrt(diag(vcov(data_veberod_2022_selection_models_linear$Always_Caged))[6]),
                          sqrt(diag(vcov(data_veberod_2022_selection_models_linear$Always_Caged))[7]),
                          sqrt(diag(vcov(data_veberod_2022_selection_models_linear$Always_Caged))[8])),
             p = c(summary(data_veberod_2022_selection_models_linear$Open_Control)$tTable[,"p-value"][2],
                   summary(data_veberod_2022_selection_models_linear$Open_Control)$tTable[,"p-value"][3],
                   summary(data_veberod_2022_selection_models_linear$Open_Control)$tTable[,"p-value"][4],
                   summary(data_veberod_2022_selection_models_linear$Open_Control)$tTable[,"p-value"][5],
                   summary(data_veberod_2022_selection_models_linear$Open_Control)$tTable[,"p-value"][6],
                   summary(data_veberod_2022_selection_models_linear$Open_Control)$tTable[,"p-value"][7],
                   summary(data_veberod_2022_selection_models_linear$Open_Control)$tTable[,"p-value"][8],
                   summary(data_veberod_2022_selection_models_linear$Day_Caged)$tTable[,"p-value"][2],
                   summary(data_veberod_2022_selection_models_linear$Day_Caged)$tTable[,"p-value"][3],
                   summary(data_veberod_2022_selection_models_linear$Day_Caged)$tTable[,"p-value"][4],
                   summary(data_veberod_2022_selection_models_linear$Day_Caged)$tTable[,"p-value"][5],
                   summary(data_veberod_2022_selection_models_linear$Day_Caged)$tTable[,"p-value"][6],
                   summary(data_veberod_2022_selection_models_linear$Day_Caged)$tTable[,"p-value"][7],
                   summary(data_veberod_2022_selection_models_linear$Day_Caged)$tTable[,"p-value"][8],
                   summary(data_veberod_2022_selection_models_linear$Night_Caged)$tTable[,"p-value"][2],
                   summary(data_veberod_2022_selection_models_linear$Night_Caged)$tTable[,"p-value"][3],
                   summary(data_veberod_2022_selection_models_linear$Night_Caged)$tTable[,"p-value"][4],
                   summary(data_veberod_2022_selection_models_linear$Night_Caged)$tTable[,"p-value"][5],
                   summary(data_veberod_2022_selection_models_linear$Night_Caged)$tTable[,"p-value"][6],
                   summary(data_veberod_2022_selection_models_linear$Night_Caged)$tTable[,"p-value"][7],
                   summary(data_veberod_2022_selection_models_linear$Night_Caged)$tTable[,"p-value"][8],
                   summary(data_veberod_2022_selection_models_linear$Always_Caged)$tTable[,"p-value"][2],
                   summary(data_veberod_2022_selection_models_linear$Always_Caged)$tTable[,"p-value"][3],
                   summary(data_veberod_2022_selection_models_linear$Always_Caged)$tTable[,"p-value"][4],
                   summary(data_veberod_2022_selection_models_linear$Always_Caged)$tTable[,"p-value"][5],
                   summary(data_veberod_2022_selection_models_linear$Always_Caged)$tTable[,"p-value"][6],
                   summary(data_veberod_2022_selection_models_linear$Always_Caged)$tTable[,"p-value"][7],
                   summary(data_veberod_2022_selection_models_linear$Always_Caged)$tTable[,"p-value"][8]))
```

```{r}
data_veberod_2022_selection_gradients <- data_veberod_2022_selection_gradients %>% 
  mutate_if(is.numeric,
            round,
            digits = 4)
```

```{r}
data_veberod_2022_selection_gradients <- data_veberod_2022_selection_gradients %>% 
  mutate(Significant = ifelse(p >= 0.05 & p <= 0.10, paste0(expression("\u2020")),
                              ifelse(data_veberod_2022_selection_gradients$p < 0.05 & data_veberod_2022_selection_gradients$p > 0.01, "*",
                                     ifelse(data_veberod_2022_selection_gradients$p < 0.01 & data_veberod_2022_selection_gradients$p > 0.001, "**",
                                            ifelse(data_veberod_2022_selection_gradients$p < 0.001, "***", "")))))
```

```{r}
data_veberod_2022_selection_gradients <- left_join(data_veberod_2022_selection_gradients,
                                                   data_veberod_2022_summary_traits,
                                              by = c("Treatment" = "Treatment",
                                                     "Trait" = "Trait"))
```

```{r}
data_veberod_2022_selection_gradients <- data_veberod_2022_selection_gradients %>% 
  mutate(Mean_Selection_Gradient = round(Estimate * Trait_Mean, digits = 4)) %>% 
  mutate(Mean_SE_Selection_Gradient = round(SE_Model * Trait_Mean, digits = 4)) %>% 
  mutate(Population = "Veberod_2022")
```

```{r}
saveRDS(data_veberod_2022_selection_gradients, 
        file = paste0(here::here("GitHub/Data/Selection_Gradients_Veberod_2022.rds")))
```